\quizheader

\qpaper{0}{Предисловие}

\qstart{Каково название нашего мира?}
{Марс}{0}
{Венера}{0}
{Урантия}{1}
{Урания}{0}
{Планета обезьян}{0}
\qstop

\qstart{Какова цель Пятого Эпохального Откровения?}
{свергнуть все религии}{0}
{расширить космическое сознание и усилить духовное восприятие}{1}
{ускорить прогресс}{0}
{сделать людей счастливыми}{0}
{ответить на вопрос <<Что будет после смерти?>>}{0}
\qstop

\qstart{Язык оригинала Пятого Эпохального Откровения\ldots}
{Армянский}{0}
{Русский}{0}
{Английский}{1}
{Мандарин}{0}
{Немецкий}{0}
{Турецкий}{0}
{Аяпанский (Nuumte Oote)}{0}
\qstop

\qstart{Кто является источником личности?}
{Всеобщий Отец}{1}
{Вечный Сын}{0}
{Бесконечный Дух}{0}
{Бог Семичастный}{0}
{Райские Сыны Создатели}{0}
\qstop

\qstart{Каково название нашей локальной вселенной?}
{Орвонтон}{0}
{Небадон}{1}
{Уверса}{0}
{Урантия}{0}
\qstop

\qstart{Каково название нашей сверхвселенной?}
{Орвонтон}{1}
{Небадон}{0}
{Уверса}{0}
{Урантия}{0}
\qstop

\qstart{Назовите столицу нашей сверхвселенной.}
{Орвонтон}{0}
{Небадон}{0}
{Уверса}{1}
{Урантия}{0}
\qstop

\qstart{Сколько обитаемых сверхвселенных в великой вселенной?}
{1}{0}
{7}{1}
{1000}{0}
{миллиарды}{0}
\qstop

\qstart{Как называется центральная вечная вселенная?}
{Рай}{0}
{Небеса}{0}
{Хавона}{1}
{Уверса}{0}
{Урантия}{0}
\qstop

\qstart{Семь сверхвселенных вместе с центральной вселенной называются\ldots}
{великая вселенная}{1}
{главная вселенная}{0}
{тотальная вселенная}{0}
{совокупная вселенная}{0}
{мироздание}{0}
\qstop

\qstart{Необитаемые вселенные внешнего пространства являются частью\ldots}
{великой вселенной}{0}
{главной вселенной}{1}
{тотальной вселенной}{0}
{совокупной вселенной}{0}
{мироздания}{0}
{Острова Рай}{0}
{вселенной Небадон}{0}
\qstop

\qstart{Объединяющее характеристическое качество Божества воспринимается созданиями как\ldots}
{совершенство}{0}
{разумность}{0}
{мудрость}{0}
{божественность}{1}
{красота}{0}
{истина}{0}
{доброта}{0}
\qstop

\qstart{Божественность воспринимается созданиями как\ldots}
{разум, дух, материя}{0}
{любовь, милосердие, служение}{0}
{время, пространство, энергия}{0}
{истина, красота, доброта}{1}
{справедливость, могущество, полновластие}{0}
\qstop

\qstart{Божественность соотносится в личности как\ldots}
{любовь, милосердие, служение}{1}
{справедливость, могущество, полновластие}{0}
{время, пространство, энергия}{0}
{истина, красота, доброта}{0}
{разум, дух, материя}{0}
\qstop

\qstart{Божественность раскрывается на безличностных уровнях как\ldots}
{любовь, милосердие, служение}{0}
{справедливость, могущество, полновластие}{1}
{время, пространство, энергия}{0}
{истина, красота, доброта}{0}
{разум, дух, материя}{0}
\qstop

\qstart{Какой из этих функциональных уровней соответствует самораспространяющемуся и отождествляемому с созданиями Божеству?}
{Статический}{0}
{Потенциальный}{0}
{Ассоциативный}{0}
{Созидательный}{0}
{Эволюционный}{1}
{Верховный}{0}
{Предельный}{0}
\qstop

\qstart{Какой из этих функциональных уровней соответствует обладающему своей волей и целью Божеству?}
{Статический}{0}
{Потенциальный}{1}
{Ассоциативный}{0}
{Созидательный}{0}
{Эволюционный}{0}
{Верховный}{0}
{Предельный}{0}
\qstop

\qstart{Какой из этих функциональных уровней соответствует самоэмпирическому, объединяющему создания и Создателя Божеству?}
{Статический}{0}
{Потенциальный}{0}
{Ассоциативный}{0}
{Созидательный}{0}
{Эволюционный}{0}
{Верховный}{1}
{Предельный}{0}
\qstop

\qstart{Какой из этих функциональных уровней соответствует самоперсонализованному и божественно братскому Божеству?}
{Статический}{0}
{Потенциальный}{0}
{Ассоциативный}{1}
{Созидательный}{0}
{Эволюционный}{0}
{Верховный}{0}
{Предельный}{0}
\qstop

\qstart{Какой из этих функциональных уровней соответствует автономному и существующему само по себе Божеству?}
{Статический}{1}
{Потенциальный}{0}
{Ассоциативный}{0}
{Созидательный}{0}
{Эволюционный}{0}
{Верховный}{0}
{Предельный}{0}
\qstop

\qstart{Какой из этих функциональных уровней соответствует самопроецирующему и превосходящему пространство\hyp{}время Божеству?}
{Статический}{0}
{Потенциальный}{0}
{Ассоциативный}{0}
{Созидательный}{0}
{Эволюционный}{0}
{Верховный}{0}
{Предельный}{1}
\qstop

\qstart{Какой из этих функциональных уровней соответствует самораспределяющемуся и божественно раскрываемому Божеству?}
{Статический}{0}
{Потенциальный}{0}
{Ассоциативный}{0}
{Созидательный}{1}
{Эволюционный}{0}
{Верховный}{0}
{Предельный}{0}
\qstop

\qstart{Божество, функционирующее на первом уровне отождествления с созданиями в качестве пространственно\hyp{}временн\'ых сверхуправляющих великой вселенной, обозначается как\ldots}
{Верховность Божества}{1}
{Предельность Божества}{0}
\qstop

\qstart{Божество, функционирующее на втором уровне выражения объединяющей божественности в качестве эффективных сверхуправляющих и абсонитных вседержителей главной вселенной, обозначается как\ldots}
{Верховность Божества}{0}
{Предельность Божества}{1}
\qstop

\qstart{Какой из уровней реальности характеризуется пространственно\hyp{}временн\'ыми ограничениями?}
{конечный}{1}
{абсонитный}{0}
{абсолютный}{0}
\qstop

\qstart{На каком уровне реальности можно превзойти пространство и время?}
{конечном}{0}
{абсонитном}{1}
{абсолютном}{0}
\qstop

\qstart{Какой из уровней реальности не зависит ни от пространства, ни от времени?}
{конечный}{0}
{абсонитный}{0}
{абсолютный}{1}
\qstop

\qstart{Является ли Божество источником всего божественного?}
{Да}{1}
{Нет}{0}
\qstop

\qstart{Обязательно ли является Божеством всё то, что является божественным?}
{Да}{0}
{Нет}{1}
\qstop

\qstart{Стремится ли всё то, что является божественным к единству с Божеством?}
{Да}{1}
{Нет}{0}
\qstop

\qstart{Божества, вечные в прошлом, настоящем и будущем известны как\ldots}
{эмпирические}{0}
{экзистенциальные}{1}
\qstop

\qstart{Божества, появляющиеся в пост\hyp{}Хавонском настоящем известны как\ldots}
{эмпирические}{1}
{экзистенциальные}{0}
\qstop

\qstart{На каком уровне реальности проявляются Райские смыслы и ценности?}
{конечном}{0}
{абсонитном}{0}
{абсолютном}{1}
\qstop

\qstart{Какой из Семи Абсолютов содержит потенциалы личностной реальности?}
{Всеобщий Отец}{0}
{Вечный Сын}{0}
{Бесконечный Дух}{0}
{Остров Рай}{0}
{Божество Абсолют}{1}
{Всеобщий Абсолют}{0}
{Безусловный Абсолют}{0}
\qstop

\qstart{Какой из Семи Абсолютов содержит потенциалы неперсонализуемой реальности?}
{Всеобщий Отец}{0}
{Вечный Сын}{0}
{Бесконечный Дух}{0}
{Остров Рай}{0}
{Божество Абсолют}{0}
{Всеобщий Абсолют}{0}
{Безусловный Абсолют}{1}
\qstop

\qstart{Какой из Семи Абсолютов демонстрирует абсолютную и бесконечную личность?}
{Всеобщий Отец}{0}
{Вечный Сын}{1}
{Бесконечный Дух}{0}
{Остров Рай}{0}
{Божество Абсолют}{0}
{Всеобщий Абсолют}{0}
{Безусловный Абсолют}{0}
\qstop

\qstart{Какой из Семи Абсолютов является первичным?}
{Всеобщий Отец}{1}
{Вечный Сын}{0}
{Бесконечный Дух}{0}
{Остров Рай}{0}
{Божество Абсолют}{0}
{Всеобщий Абсолют}{0}
{Безусловный Абсолют}{0}
\qstop

\qstart{Какой из Семи Абсолютов делает возможным сосуществование конечного и бесконечного?}
{Всеобщий Отец}{0}
{Вечный Сын}{0}
{Бесконечный Дух}{0}
{Остров Рай}{0}
{Божество Абсолют}{0}
{Всеобщий Абсолют}{1}
{Безусловный Абсолют}{0}
\qstop

\qstart{Настройщики Мыслей являются\ldots}
{личностными}{0}
{доличностными}{1}
{сверхличностными}{0}
{субличностными}{0}
\qstop

\qstart{Где сходятся линии гравитации духовного контура?}
{во Всеобщем Отце}{0}
{в Вечном Сыне}{1}
{в Бесконечном Духе}{0}
\qstop

\qstart{Можно ли измерить духовную гравитацию?}
{Да}{1}
{Нет}{0}
\qstop

\qstart{Как обнаружить присутствие личности в живой системе?}
{по тесту Тьюринга}{0}
{по наличию сознания}{0}
{по реакции на личностный контур Отца}{1}
{по способности решать математические задачи}{0}
\qstop

\qstart{Как обнаружить присутствие духа в живой системе?}
{по тесту Тьюринга}{0}
{по реакции на духовный контур Сына}{1}
{по стремлению любить и быть любимым}{0}
{по умению философствовать}{0}
{по умению становиться невидимым}{0}
\qstop

\qstart{Что такое материя?}
{всё то, что видимо человеческому глазу}{0}
{всё то, что реагирует на контур материальной гравитации с центром в нижнем Раю}{1}
{всё то, что подвержено разрушительному действию времени}{0}
\qstop


\qstart{Когда была создана центральная вселенная Хавона?}
{500 миллиардов лет назад}{0}
{6.000 лет назад}{0}
{она существовала вечно}{1}
{9 миллиардов лет назад}{0}
\qstop

\qstart{Что является посредником между материей и духом в области актуальной реальности?}
{Бог}{0}
{Настройщик Мыслей}{0}
{ангелы}{0}
{разум}{1}
\qstop

\qpaper{1}{Всеобщий Отец}

\qstart{Что является самым ценным даром человека Богу?}
{золото и серебро в больших количествах}{0}
{трансцендентальная медитация}{0}
{подаяние милостыни нищим}{0}
{посвящение своей воли исполнению воли Отца}{1}
{молитва пять раз в день}{0}
\qstop

\endinput

\qpaper{2}{The Nature of God}

\qstart{Truth is...}
{living and flexible}{1}
{best known by its spiritual flavour}{1}
{coherent, beauty attractive, goodness stabilizing}{1}
{alive, free, thrilling, and always moving}{0}
\qstop

\qpaper{3}{The Attributes of God}

\qpaper{4}{God’s Relation to the Universe}

\qstart{The atonement doctrine is a...}
{divinely inspired and true doctrine}{0}
{affront and insult to God}{1}
\qstop

\qstart{Who forbade the Hebrews to perform the human sacrifices?}
{Abraham}{0}
{Moses}{1}
{Joshua}{0}
{Jesus}{0}
{Paul}{0}
{Peter}{0}
\qstop

\qpaper{5}{God’s Relation to the Individual}

\qpaper{6}{The Eternal Son}

\qstart{Which of these is the capital of our local universe?}
{Salvington}{1}
{Edentia}{0}
{Uversa}{0}
{Jerusem}{0}
\qstop

\qstart{Does the Eternal Son fragmentize his nature like the Universal Father?}
{no}{1}
{yes}{0}
\qstop

\qstart{Does the Eternal Son bestow personality?}
{no}{1}
{yes}{0}
\qstop

\qstart{Is the Eternal Son omnipotent?}
{only in the spiritual realm}{1}
{only in the physical realm}{0}
{yes, in both physical and spiritual realms}{0}
\qstop

\qstart{Is the Eternal Son omniscient (all-knowing)?}
{yes}{1}
{no}{0}
\qstop

\qstart{Can the Creator Sons transmit the prerogatives of creatorship?}
{yes}{0}
{no}{1}
\qstop

\qpaper{7}{Relation of the Eternal Son to the Universe}

\qstart{Can the Eternal Son contact directly with human beings as the Father does through the gift of the prepersonal Thought Adjusters?}
{yes}{0}
{no}{1}
\qstop

\qstart{Did the bestowals of the Eternal Son in Havona add to the supposed experiential capacity of his existential nature?}
{yes}{0}
{no}{0}
{we do not know, because this would fall within the bestowal mystery of the Paradise Sons}{1}
\qstop

\qstart{Does the Eternal Son fully comprehend the eternal plan of the Universal Father for the universe of universes?}
{yes}{1}
{no}{0}
\qstop

\qstart{Does spirit gravity suffer time delays?}
{yes}{0}
{no}{1}
\qstop

\qstart{Does spirit gravity undergo space diminution?}
{yes}{0}
{no}{1}
\qstop

\qstart{The transcendence of time and space by pure spirit energies is...}
{due to the interposition of the antigravity forces of the Third Source and Centre}{0}
{inherent in the absoluteness of the Eternal Son}{1}
\qstop

\qpaper{8}{The Infinite Spirit}

\qstart{Which of the Paradise Deities is the first to be attained by the ascending pilgrims?}
{Universal Father}{0}
{Eternal Son}{0}
{Infinite Spirit}{1}
\qstop

\qstart{God is love, the Son is mercy, the Spirit is...}
{law}{0}
{obedience}{0}
{peace}{0}
{ministry}{1}
\qstop

\qstart{Is the Conjoint Creator omnipotent?}
{yes}{0}
{no}{0}
{only in the domain of mind}{1}
\qstop

\qpaper{9}{Relation of the Infinite Spirit to the Universe}

\qstart{Who or what is the apparent ancestor of motion, change, and relationship?}
{Paradise}{0}
{Havona}{0}
{Eternal Son}{0}
{God of Action (The Third Source and Centre)}{1}
\qstop

\qstart{Is the power of antigravity observably present in either the Universal Father or the Eternal Son?}
{yes}{0}
{no}{1}
\qstop

\qstart{Is the gravity-resistant phenomenon of a gyroscope of value to illustrate the effect of antigravity?}
{yes}{1}
{no}{0}
\qstop

\qstart{Is the gravity-resistant phenomenon of a gyroscope of value to illustrate the cause of antigravity?}
{yes}{0}
{no}{1}
\qstop

\qstart{Which of these is a typical use of antigravity in the grand universe?}
{establish physical equilibrium of the matter and energies}{1}
{transport}{0}
{overriding natural course of events on evolutionary worlds}{0}
{amusement of the Deities}{0}
\qstop

\qstart{Is mind inherent in energy?}
{yes}{0}
{no}{1}
\qstop

\qstart{Is spirit always intelligent, i.e. minded in some way?}
{yes}{1}
{not necessarily}{0}
\qstop

\qstart{Is the Conjoint Creator absolute?}
{yes}{0}
{no}{0}
{only in the realms of universal intelligence}{1}
\qstop

\qstart{What is the source of the mind endowment of the seven superuniverses?}
{Seven Master Spirits}{1}
{Seven Supreme Executives}{0}
{Architects of the Master Universe}{0}
{Ancients of Days}{0}
{The Infinite Spirit}{0}
\qstop

\qstart{Energy is thing, mind is meaning, spirit is...}
{value}{1}
{substance}{0}
{destiny}{0}
{light}{0}
\qstop

\qpaper{10}{The Paradise Trinity}

\qstart{What does facilitate the Father's escape from personality absolutism?}
{The Isle of Paradise}{0}
{The Paradise Trinity}{1}
{The Eternal Son}{0}
{The Infinite Spirit}{0}
\qstop

\qstart{Is the Paradise Trinity inevitable?}
{Yes}{1}
{No}{0}
\qstop

\qstart{Does the Supreme Being exhaust the totality of Trinity's attitude towards the finite?}
{Yes}{0}
{No}{1}
\qstop

\qstart{Does the Ultimate exhaust the totality of Trinity's attitude towards the absonite?}
{Yes}{0}
{No}{1}
\qstop

\qstart{Will the finaliters ever attain the Deity Absolute?}
{Yes}{0}
{No}{0}
{Maybe}{1}
\qstop

\qpaper{11}{The Eternal Isle of Paradise}

\qstart{How many outer space levels are there?}
{3}{0}
{4}{1}
{7}{0}
{12}{0}
{1}{0}
\qstop

\qstart{Which area of the upper Paradise does the Father reside in?}
{Deity presence}{1}
{Most Holy Sphere}{0}
{Holy Area}{0}
\qstop

\qstart{How long is the complete cycle of spare respiration?}
{2 billion years}{1}
{1 billion years}{0}
{100 billion years}{0}
{500 million years}{0}
{6000 years}{0}
\qstop

\qstart{Which of these are the three planes or domains of activity in Paradise?}
{Upper Paradise}{1}
{Nether Paradise}{1}
{Peripheral Paradise}{1}
{Central Paradise}{0}
{Inner Paradise}{0}
\qstop

\qstart{Which plane of Paradise is dominated by the Trinity?}
{Upper}{1}
{Nether}{0}
{Peripheral}{0}
\qstop

\qstart{How many grand spheres of activity are on upper Paradise?}
{3}{1}
{7}{0}
{12}{0}
{24}{0}
{4}{0}
\qstop

\qstart{How many planes or domains of activity are there in Paradise?}
{3}{1}
{4}{0}
{7}{0}
{12}{0}
{Infinitely many}{0}
\qstop

\qstart{Which of these are the grand spheres of activity on upper Paradise?}
{Most Holy Sphere}{1}
{Holy Area}{1}
{Deity presence}{1}
{Trinity Centre}{0}
\qstop

\qstart{Is the Most Holy Sphere of Paradise...}
{wholly spiritual}{1}
{wholly material}{0}
{partly spiritual and partly material}{0}
{neither spiritual nor material}{0}
\qstop

\qstart{Is it possible to establish absolute direction in the master universe?}
{No, it is isotropic}{0}
{Yes, using the out-pressure of force-energy at the north end of the Isle of Paradise}{1}
{Unknown}{0}
\qstop

\qstart{Where does space seemingly originate?}
{just below nether Paradise}{1}
{just above upper Paradise}{0}
{around peripheral Paradise}{0}
\qstop

\qstart{Is motion inherent or volitional on Paradise?}
{inherent}{0}
{volitional}{1}
\qstop

\qstart{Can the concept of distance be applied to locations on Paradise?}
{yes}{1}
{no}{0}
\qstop

\qstart{Can the concept of space be applied to locations on Paradise?}
{no}{1}
{yes}{0}
\qstop

\qstart{Is time (as mortals understand it) a feature of Paradise existence?}
{no}{1}
{yes}{0}
\qstop

\qstart{Do personalities sojourn on nether Paradise?}
{no}{1}
{yes}{0}
\qstop

\qstart{What presence dominates on nether Paradise?}
{Unqualified Absolute}{1}
{Deity Absolute}{0}
{Universal Absolute}{0}
{God the Sevenfold}{0}
{God the Supreme}{0}
\qstop

\qstart{What is the relation between Paradise and space-time?}
{Paradise exists without time and has no location in space}{1}
{Paradise exists at a definite location in space, but has no time}{0}
{Paradise exists at a definite location in space and has time}{0}
{Paradise has no location in space, but has time}{0}
\qstop

\qstart{Does cosmic force respond to mind?}
{no}{0}
{yes}{1}
\qstop

\qstart{What is the source of absolute gravity?}
{Paradise}{1}
{mind}{0}
{matter}{0}
{spirit}{0}
\qstop

\qstart{Is Paradise substance (absoluta) dead or alive?}
{Dead}{0}
{Alive}{0}
{Neither dead nor alive}{1}
\qstop

\qstart{Does space respond to gravity?}
{no}{1}
{yes}{0}
\qstop

\qstart{Can pervaded space neutralize linear gravity?}
{yes}{1}
{no}{0}
\qstop

\qstart{Can pervaded space delay linear gravity?}
{yes}{0}
{no}{1}
\qstop

\qpaper{12}{The Universe of Universes}

\qstart{Why is there no universal time unit based on motion?}
{because the totality of space respiration destroys the local value of Paradise-Havona standard day as a time source}{1}
{because time is relative, depending on the moving observer's frame of reference}{0}
\qstop

\qstart{As the mind of any personality in the universe becomes more spiritual, how is its response to material gravity affected?}
{becomes more responsive}{0}
{is not affected}{0}
{becomes less responsive}{1}
\qstop

\qstart{What is the only reality in the universe that can interassociate the physical forces and energies of the material level with the spiritual powers and beings of the spirit level?}
{morontia}{0}
{spirit}{0}
{mind}{1}
{space}{0}
{matter}{0}
\qstop

\qstart{Do the beings arriving on Paradise have to become unconscious during the transit through the motionless midspace zones separating pervaded space from unpervaded?}
{yes, during every trip to Paradise}{0}
{no, never}{0}
{yes, but only if the transit is to culminate in Paradise citizenship (as opposed to mere visitors who remain creatures of time)}{1}
\qstop

\qstart{Does consciousness of time exist without motion in space?}
{yes}{1}
{no}{0}
\qstop

\qstart{Is time itself a genetic quality of mind?}
{yes}{0}
{no}{1}
\qstop

\qstart{Does time come by virtue of motion or because mind is inherently aware of sequentiality?}
{by virtue of motion}{0}
{because mind is inherently aware of sequentiality}{0}
{both}{1}
\qstop

\qstart{Which of these are the three levels of time cognizance?}
{Mind-perceived time --- consciousness of sequence, motion, and a sense of duration}{1}
{Spirit-perceived time --- insight into motion Godward and the awareness of the motion of ascent to levels of increasing divinity}{1}
{Personality sense of time created out of insight into Reality plus a consciousness of presence and an awareness of duration}{1}
{Coordinate time as measured by the clock attached to a given moving observer's frame of reference}{0}
\qstop

\qstart{Is the Andromeda Galaxy (M31) inside or outside the space level of superuniverses?}
{inside}{0}
{outside}{1}
{exactly on the border}{0}
\qstop

\qstart{The absolute of time is eternity and the absolute of space is...}
{unknown}{1}
{infinite and unlimited space}{0}
\qstop

\qstart{Are time and space inseparable?}
{yes, everywhere}{0}
{only in the seven superuniverses}{1}
\qstop

\qstart{Which types of space motion are absolute?}
{alternate directional swings of the successive space levels}{1}
{space respiration}{1}
{compensatory or correlating movement}{0}
\qstop

\qstart{Is personality gravity computable?}
{yes}{0}
{no}{1}
\qstop

\qstart{How much of the mind gravity is focused in the existing grand universe?}
{1\%}{0}
{10\%}{0}
{50\%}{0}
{60\%}{0}
{85\%}{1}
{95\%}{0}
\qstop

\qstart{How much of the mind gravity is focused in the creations of the outer space levels?}
{1\%}{0}
{10\%}{0}
{15\%}{1}
{25\%}{0}
{60\%}{0}
{80\%}{0}
\qstop

\qstart{How much of the cosmic-gravity action of the Isle of Paradise is engaged in controlling material systems beyond the borders of the present organized universes?}
{95\%}{1}
{1\%}{0}
{50\%}{0}
{25\%}{0}
{85\%}{0}
\qstop

\qstart{Which of these are the absolute gravity circuits in the master universe?}
{The Personality Gravity of the Universal Father}{1}
{The Spirit Gravity of the Eternal Son}{1}
{The Mind Gravity of the Conjoint Actor}{1}
{The Cosmic Gravity of the Isle of Paradise}{1}
{The Linear Gravity of the electronic stage of matter organization}{0}
\qstop

\qstart{Are the four absolute gravity circuits independent of time and space?}
{yes}{1}
{no}{0}
\qstop

\qstart{How much of the spirit gravity is functioning in the grand universe?}
{100\%}{1}
{50\%}{0}
{25\%}{0}
{95\%}{0}
{75\%}{0}
\qstop

\qpaper{13}{The Sacred Spheres of Paradise}

\qstart{Which of these are forever forbidden to us?}
{Divinington}{1}
{nether Paradise}{1}
{the seven sacred Paradise satellites of the Son}{1}
{Paradise}{0}
{Uversa}{0}
{Sonarington}{0}
{Ascendington}{0}
\qstop

\qstart{What are the executuve-headquarters of the Seven Master Spirits?}
{seven sacred spheres of the Infinite Spirit}{1}
{seven sacred spheres of the Universal Father}{0}
{seven sacred spheres of the Eternal Son}{0}
{Urantia, Mercury, Venus, Mars, and Pluto}{0}
\qstop

\qstart{Which material is used in the physical construction of the 21 sacred spheres of Paradise?}
{unrevealed}{1}
{mostly gold, iron, and some carbon in crystallised state}{0}
{morontia materials}{0}
{spirit}{0}
\qstop

\qstart{Where is the record of the origin of the 21 sacred spheres of Paradise stored?}
{in the Most Holy area of upper Paradise}{0}
{in the nether Paradise}{0}
{on one of the billion perfect worlds of Havona}{0}
{nowhere, it doesn't exist}{1}
\qstop

\qstart{Which of the 21 sacred spheres of Paradise are alike in physical constitution?}
{the seven worlds of the Son}{1}
{the seven worlds of the Father}{0}
{the seven worlds of the Spirit}{0}
\qstop

\qstart{What kind of personal beings may sojourn on the seven sacred spheres of the Eternal Son?}
{none}{1}
{Seven Master Spirits}{0}
{Architects of the Master Universe}{0}
{only beings endowed with antigravity power}{0}
\qstop

\qstart{When are you granted clearance for Ascendington?}
{upon attaining Havona}{1}
{upon attaining Uversa}{0}
{upon graduation from the Melchizedek schools}{0}
{upon resurrection from the dead}{0}
{upon fusion with the Thought Adjuster}{0}
\qstop

\qstart{Which of the sacred spheres of the Father is the Paradise rendezvous of the Thought Adjusters?}
{Divinington}{1}
{Sonarington}{0}
{Spiritington}{0}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{0}
{Ascendington}{0}
\qstop

\qstart{What kind of beings function on Divinington?}
{Father fragments (such as Thought Adjusters) and other beings of direct origin in the Universal Father}{1}
{beings of unrevealed order}{0}
{Architects of the Master Universe}{0}
{Seven Master Spirits}{0}
{Paradise Creator Sons}{0}
\qstop

\qstart{Which of these are among the secrets of Divinington?}
{secret of the bestowal and mission of Thought Adjusters}{1}
{nature and purpose of the Gravity Messengers}{1}
{secret of the incarnation of the divine Sons}{0}
{mysteries of reflectivity}{0}
{secrets of trinitization}{0}
{mystery of seraphic transport}{0}
\qstop

\qstart{When were the 21 sacred spheres of Paradise created?}
{1 trillion years ago}{0}
{9 billion years ago}{0}
{250 billion years ago}{0}
{never, they are eternal}{1}
\qstop

\qstart{How many of the 21 sacred spheres of Paradise illuminate both the Havona and the Isle of Paradise?}
{0}{0}
{7}{0}
{14}{1}
{21}{0}
\qstop

\qstart{How many of the 21 sacred spheres of Paradise illuminate only the Havona but \bibemph{not} the Isle of Paradise?}
{0}{0}
{7}{1}
{14}{0}
{21}{0}
\qstop

\qstart{How many of the 21 sacred spheres of Paradise illuminate only the Isle of Paradise but not the Havona?}
{0}{1}
{7}{0}
{14}{0}
{21}{0}
\qstop

\qstart{Which of the 21 sacred spheres of Paradise illuminate both the Havona and the Isle of Paradise?}
{worlds of the Father}{1}
{worlds of the Son}{1}
{worlds of the Spirit}{0}
\qstop

\qstart{Which of the 21 sacred spheres of Paradise illuminate only the Havona but not the Isle of Paradise?}
{worlds of the Father}{0}
{worlds of the Son}{0}
{worlds of the Spirit}{1}
\qstop

\qstart{Who directs the seven Paradise sacred spheres of the Father?}
{Trinitized Secrets of Supremacy}{1}
{Seven Master Spirits}{0}
{Trinity Teacher Sons}{0}
{Melchizedeks}{0}
{Ancients of Days}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Father''?}
{Divinington}{1}
{Sonarington}{0}
{Spiritington}{0}
{Ascendington}{0}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Son''?}
{Divinington}{0}
{Sonarington}{1}
{Spiritington}{0}
{Ascendington}{0}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Spirit''?}
{Divinington}{0}
{Sonarington}{0}
{Spiritington}{1}
{Ascendington}{0}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Father and the Son''?}
{Divinington}{0}
{Sonarington}{0}
{Spiritington}{0}
{Ascendington}{0}
{Vicegerington}{1}
{Solitarington}{0}
{Seraphington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Father and the Spirit''?}
{Divinington}{0}
{Sonarington}{0}
{Spiritington}{0}
{Ascendington}{0}
{Vicegerington}{0}
{Solitarington}{1}
{Seraphington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Father, Son, and Spirit''?}
{Divinington}{0}
{Sonarington}{0}
{Spiritington}{0}
{Ascendington}{1}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father can be called ``the bosom of the Son and the Spirit''?}
{Divinington}{0}
{Sonarington}{0}
{Spiritington}{0}
{Ascendington}{0}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{1}
\qstop

\qstart{Which of these are among the secrets of Sonarington?}
{secret of the bestowal and mission of Thought Adjusters}{0}
{nature and purpose of the Gravity Messengers}{0}
{secret of the incarnation of the divine Sons}{1}
{mysteries of reflectivity}{0}
{secrets of trinitization}{0}
{mystery of seraphic transport}{0}
\qstop

\qstart{Which of these are among the secrets of Seraphington?}
{secret of the bestowal and mission of Thought Adjusters}{0}
{nature and purpose of the Gravity Messengers}{0}
{secret of the incarnation of the divine Sons}{0}
{mysteries of reflectivity}{0}
{secrets of trinitization}{0}
{mystery of seraphic transport}{1}
\qstop

\qstart{Which sector of Sonarington is the secret of incarnation locked in?}
{seventh}{1}
{first}{0}
{third}{0}
{fifth}{0}
\qstop

\qstart{Which of these are among the secrets of Spiritington?}
{secret of the bestowal and mission of Thought Adjusters}{0}
{nature and purpose of the Gravity Messengers}{0}
{secret of the incarnation of the divine Sons}{0}
{mysteries of reflectivity}{1}
{secrets of trinitization}{0}
{mystery of seraphic transport}{0}
\qstop

\qstart{Which of these are among the secrets of Vicegerington?}
{secret of the bestowal and mission of Thought Adjusters}{0}
{nature and purpose of the Gravity Messengers}{0}
{secret of the incarnation of the divine Sons}{0}
{mysteries of reflectivity}{0}
{secrets of trinitization}{1}
{mystery of seraphic transport}{0}
\qstop

\qstart{Which of the sacred spheres of the Father is the home of Solitary Messengers?}
{Solitarington}{1}
{Vicegerington}{0}
{Sonarington}{0}
{Seraphington}{0}
{Ascendington}{0}
\qstop

\qstart{Which of the sacred spheres of the Father is the status sphere of the Universe Power Directors during the present universe age?}
{Solitarington}{1}
{Vicegerington}{0}
{Sonarington}{0}
{Seraphington}{0}
{Ascendington}{0}
\qstop

\qstart{Which of these are among the secrets of Solitarington?}
{secret of the bestowal and mission of Thought Adjusters}{0}
{nature and purpose of the Gravity Messengers}{0}
{secret of the incarnation of the divine Sons}{0}
{mysteries of reflectivity}{0}
{secrets of trinitization}{1}
{the secrets of the personal relation of the Infinite Spirit with certain of the higher offspring of the Third Source and Center}{1}
\qstop

\qstart{Which of these are among the secrets of Ascendington?}
{secret of the bestowal and mission of Thought Adjusters}{0}
{nature and purpose of the Gravity Messengers}{0}
{secret of the incarnation of the divine Sons}{0}
{mysteries of reflectivity}{0}
{secrets of trinitization}{0}
{mystery of the evolution of an immortal soul within the mind of a mortal and material creature}{1}
\qstop

\qstart{Which of the seven sacred spheres of the Father will become fully open to our inspection?}
{Divinington}{0}
{Sonarington}{0}
{Spiritington}{0}
{Ascendington}{1}
{Vicegerington}{0}
{Solitarington}{0}
{Seraphington}{0}
\qstop

\qstart{How many Trinitized Secrets of Supremacy direct Ascendington?}
{10}{1}
{12}{0}
{7}{0}
{3}{0}
\qstop

\qstart{Who knows all the secrets of all seven Paradise sacred spheres of the Father?}
{Trinitized Secrets of Supremacy}{1}
{Seven Master Spirits}{0}
{Trinity Teacher Sons}{0}
{Melchizedeks}{0}
{Ancients of Days}{0}
\qstop

\qpaper{14}{The Central and Divine Universe}

\qstart{Our material bodies have five physical senses, how many senses does a morontia body have, in potential?}
{7}{0}
{10}{0}
{36}{0}
{70}{1}
{77}{0}
{100}{0}
\qstop

\qstart{What is the number of elements on the architectural spheres compared to those on the evolutionary planets?}
{half as many}{0}
{twice as many}{1}
{the same number}{0}
\qstop

\qstart{How many perfect spheres does Havona consist of?}
{100 billion}{0}
{500 million}{0}
{1 billion}{1}
{144000}{0}
{7}{0}
{12}{0}
\qstop

\qstart{Select all space conditions that exist from the periphery of Paradise to the inner borders of the seven superuniverses?}
{The clockwise processional of the three Paradise and the seven Havona circuits}{1}
{The semiquiet space zone separating the Havona circuits from the dark gravity bodies of the central universe}{1}
{The inner, counterclockwise-moving belt of the dark gravity bodies}{1}
{The quiescent midspace zones impinging on Paradise}{1}
{The second unique space zone dividing the two space paths of the dark gravity bodies}{1}
{The outer belt of dark gravity bodies, revolving clockwise around Paradise}{1}
{A third space zone—a semiquiet zone—separating the outer belt of dark gravity bodies from the innermost circuits of the seven superuniverses}{1}
\qstop

\qstart{How many circuits are the billion worlds of Havona arranged in?}
{12}{0}
{3}{0}
{4}{0}
{1000}{0}
{1024}{0}
{7}{1}
\qstop

\qstart{How many worlds are in the innermost circuit of Havona?}
{245 million+}{0}
{25 million+}{0}
{1 million+}{0}
{35 million+}{1}
{365}{0}
\qstop

\qstart{How many worlds are in the outermost circuit of Havona?}
{35 million+}{0}
{25 million+}{0}
{245 million+}{1}
{1 million+}{0}
{365}{0}
\qstop

\qstart{Are the Havona planetary circuits superimposed?}
{yes}{0}
{no}{1}
\qstop

\qstart{Does perception of time exist on the Havona circuits?}
{yes}{1}
{no}{0}
\qstop

\qstart{Is the length of year the same on all the worlds of a given Havona circuit?}
{yes}{1}
{no}{0}
\qstop

\qstart{How does the length of year change from circuit to circuit in Havona?}
{increases from the outermost to the innermost circuit}{0}
{stays the same}{0}
{decreases from the outermost to the innermost circuit}{1}
\qstop

\qstart{Where is the length of Paradise-Havona day decided and broadcast from?}
{the seven sacred spheres of the Universal Father}{0}
{on one of the billion perfect spheres of Havona}{0}
{the seven sacred spheres of the Infinite Spirit}{1}
{Isle of Paradise}{0}
{the seven sacred spheres of the Eternal Son}{0}
\qstop

\qstart{How many planes do the three circuits of Paradise satellites and the seven circuits of Havona worlds move in?}
{seven}{0}
{ten}{0}
{one}{1}
{three}{0}
\qstop

\qstart{Based on what periodic movement is the standard Paradise-Havona day defined?}
{revolution of the outer Havona circuit around the Isle of Paradise}{0}
{average revolution of all Havona circuits around the Isle of Paradise}{0}
{arbitrarily decided by the Paradise Deities}{0}
{space respiration}{0}
{revolution of the inner Havona circuit around the Isle of Paradise}{1}
\qstop


\qstart{One Paradise-Havona day is equivalent to how much Urantia time?}
{100 years}{0}
{30 days}{0}
{1000 years}{1}
{15 days}{0}
{1 day}{0}
\qstop

\qstart{Where do the spirit beings dwell?}
{in nebulous space}{0}
{on ethereal spirit worlds}{0}
{on material spheres}{1}
\qstop

\qstart{How many basic chemical elements does the material of Havona consist of?}
{100}{0}
{256}{0}
{512}{0}
{1000}{1}
{1024}{0}
{1000000}{0}
\qstop

\qstart{How many forms of energy exist in Havona?}
{12}{0}
{49}{0}
{7}{1}
{100}{0}
{10}{0}
\qstop

\qstart{How many phases of excitation does each of the basic forms of energy in Havona manifest?}
{7}{1}
{49}{0}
{3}{0}
{1000}{0}
{4}{0}
\qstop

\qstart{How many different sensation stimuli do Havona natives respond to?}
{7}{0}
{3}{0}
{1000}{0}
{4}{0}
{49}{1}
\qstop

\qstart{How many of the 49 physical stimuli of Havona worlds would excite a reaction in Urantia mortals?}
{49}{0}
{7}{0}
{0}{1}
{5}{0}
{4}{0}
{47}{0}
\qstop

\qstart{Why are the Havona forms of energy threefold whereas the superuniverse forms of energy are twofold?}
{because the creation of Havona is threefold (Trinity) whereas the creation of local universes is twofold (Creator Son and Creative Mother Spirit)}{1}
{for unknown or unrevealed reason}{0}
\qstop

\qstart{What type of government exists on the perfect worlds of Havona?}
{none (perfection makes government unnecessary)}{1}
{democracy}{0}
{anarchy}{0}
{theocracy}{0}
{aristocracy}{0}
\qstop

\qstart{Who directs each of the billion worlds of the central universe?}
{one Eternal of Days}{1}
{three Eternals of Days}{0}
{three Ancients of Days}{0}
{one Creator Son and one Creative Mother Spirit}{0}
\qstop

\qstart{Which of these are the basic forms of living things and beings on Havona worls?}
{material}{1}
{morontial}{1}
{spiritual}{1}
{absonite}{1}
{ultimate}{1}
{coabsolute}{1}
{absolute}{1}
\qstop

\qstart{Are decay and death a part of the cycle of life on the Havona worlds?}
{yes}{0}
{no}{1}
\qstop

\qstart{Are Havona natives reproducing beings?}
{yes}{0}
{no}{1}
\qstop

\qstart{Which circuit of Havona are the new arrivals domiciled on?}
{4}{0}
{5}{0}
{2}{0}
{3}{0}
{7}{1}
{1}{0}
{6}{0}
\qstop

\qstart{Which circuit of Havona are the pilgrims transferred to when they attain identity comprehension of their superuniverse Master Spirit?}
{5}{0}
{3}{0}
{4}{0}
{6}{1}
{2}{0}
{7}{0}
{1}{0}
\qstop

\qstart{Which circuit of Havona are the pilgrims transferred to when they attain realization of Supremacy?}
{2}{0}
{1}{0}
{3}{0}
{6}{0}
{7}{0}
{4}{0}
{5}{1}
\qstop

\qstart{Which circuit of Havona are the pilgrims transferred to when they attain the Infinite Spirit?}
{4}{1}
{7}{0}
{3}{0}
{5}{0}
{1}{0}
{2}{0}
{6}{0}
\qstop

\qstart{Which circuit of Havona are the pilgrims transferred to when they attain the Eternal Son?}
{4}{0}
{7}{0}
{6}{0}
{2}{0}
{1}{0}
{3}{1}
{5}{0}
\qstop

\qstart{Which circuit of Havona are the pilgrims transferred to when they have recognized the Universal Father?}
{3}{0}
{1}{0}
{2}{1}
{6}{0}
{4}{0}
{7}{0}
{5}{0}
\qstop

\qstart{Which circuit of Havona are the pilgrims transferred to when they have been accepted into the service of Paradise?}
{7}{0}
{2}{0}
{5}{0}
{1}{1}
{4}{0}
{6}{0}
{3}{0}
\qstop

\qstart{Which of the Havona worlds can a pilgrim of ascent visit without the need to be ensupernaphimed?}
{all worlds of all circuits}{0}
{all worlds of the present circuit only}{0}
{all worlds of those circuits which have already been traversed}{1}
{none of them}{0}
\qstop

\qpaper{15}{The Seven Superuniverses}

\qstart{How many Reflective Spirits are there?}
{7}{0}
{3}{0}
{50}{1}
{49}{0}
{144000}{0}
\qstop

\qstart{Who is the chief of the Reflective Spirits?}
{Father Melchizedek}{0}
{Gabriel}{0}
{Michael of Nebadon}{0}
{Infinite Spirit}{0}
{Majeston}{1}
{Father Reflective Spirit \#1}{0}
\qstop

\qstart{How long is the standard (Uversa) day?}
{1 Urantia day}{0}
{1 Urantia year}{0}
{30 Urantia days}{1}
{1000 Urantia years}{0}
\qstop

\qstart{How long is the standard (Uversa) year?}
{365 Urantia days}{0}
{10 Urantia years}{0}
{1000 Urantia years}{0}
{3000 Urantia days}{1}
\qstop

\qstart{Which of these are superuniverse circuits?}
{The unifying intelligence circuit of one of the Seven Master Spirits of Paradise, a cosmic-mind}{1}
{The reflective-service circuit of the seven Reflective Spirits}{1}
{The secret circuits of the Mystery Monitors, routed by Divinington to the Universal Father on Paradise}{1}
{The circuit of the intercommunion of the Eternal Son with his Paradise Sons}{1}
{The flash presence of the Infinite Spirit}{1}
{The broadcasts of Paradise, the space reports of Havona}{1}
{The energy circuits of the power centres and the physical controllers}{1}
\qstop

\qstart{Which of these are the local universe circuits?}
{The bestowal spirit of the Paradise Sons, the Spirit of Truth}{1}
{The circuit of the Divine Ministers, the Holy Spirit}{1}
{The intelligence-ministry circuit, including the diversely functioning presence of the adjutant mind-spirits}{1}
\qstop

\qstart{What are the requisites for admission of a local universe to the councils of the Ancients of Days?}
{Not a single loss of Lanonandek Sons}{0}
{Physical Stability}{1}
{Spiritual Loyalty}{1}
{Reach 10,000,000 inhabited worlds}{0}
\qstop

\qstart{Is our local universe of Nebadon admitted to the councils of the Ancients of Days?}
{yes}{0}
{no}{1}
\qstop

\qstart{Is our local universe's physical order settled?}
{yes}{0}
{no}{1}
\qstop

\qstart{How many Perfectors of Wisdom are assisting the three Ancients of Days?}
{1000}{0}
{1 million}{0}
{1 billion}{1}
{7}{0}
{70}{0}
\qstop

\qstart{Does the executive branch of the superuniverse government include glorified ascendant mortals?}
{yes}{1}
{no}{0}
\qstop

\qstart{Which of these beings serve as ambassadors of one superuniverse in another?}
{Solitary Messengers}{0}
{Mighty Messengers}{0}
{Those High in Authority}{0}
{none, the superuniverses are completely isolated from each other}{1}
{Those Without Name and Number}{0}
\qstop

\qstart{What is the registry number of Urantia in the catalogue of inhabited worlds on Uversa and Paradise?}
{619}{0}
{666,666,666,666}{0}
{666}{0}
{606}{0}
{5,342,482,337,666}{1}
{5,287,480,037,666}{0}
\qstop

\qstart{Which of these are the components of the celestial coordinates of our planet in the grand universe?}
{Planet Urantia, number 606 in the system of Satania}{1}
{System of Satania (capital world Jerusem), number 24 in the constellation of Norlatiadek}{1}
{Constellation of Norlatiadek (headquarters world Edentia), number 70 in the universe of Nebadon}{1}
{Local universe of Nebadon (capital world Salvington), number 84 in the minor sector of Ensa}{1}
{Minor sector of Ensa (capital world Uminor the third), number 3 in the major sector of Splandon}{1}
{Major sector of Splandon (capital world Umajor the fifth), number 5 in the superuniverse of Orvonton}{1}
{Superuniverse of Orvonton (headquarters world Uversa), number 7 in the grand universe}{1}
\qstop

\qstart{Which of these are the units of supergovernment in the Grand Universe?}
{Planet}{0}
{System}{1}
{Constellation}{1}
{Local Universe}{1}
{Minor Sector}{1}
{Major Sector}{1}
{Superuniverse}{1}
\qstop

\qstart{When was the sevenfold scheme of the superuniverse organization and government formulated?}
{early in the materialization of the universal creation}{1}
{in the eternal past}{0}
{it was never planned, the superuniverses just evolved that way spontaneously, by chance}{0}
\qstop

\qstart{Who are the rulers of the seven evolutionary superuniverses?}
{Eternals of Days}{0}
{Ancients of Days}{1}
{Perfections of Days}{0}
{Recents of Days}{0}
{Faithfuls of Days}{0}
{Unions of Days}{0}
\qstop

\qstart{Which curve do the seven superuniverses traverse in space?}
{Circle}{0}
{Cardioid}{0}
{Archimedean Spiral}{0}
{Ellipse}{1}
{Lemniscate}{0}
{Epicycloid}{0}
{Hypocycloid}{0}
{Astroid}{0}
\qstop

\qstart{Who knows the location and name of every inhabited world in space?}
{Ancients of Days}{0}
{Architects of the Master Universe}{0}
{Paradise Creator Sons}{0}
{Universal Father}{1}
{Universal Censors}{0}
\qstop

\qstart{Each inhabited planet is presided over by ...}
{Governor General}{0}
{Planetary Prince}{1}
{Chief Archangel}{0}
{God}{0}
{Jesus Christ}{0}
{System Sovereign}{0}
\qstop

\qstart{Each local system has an architectural sphere as its headquarters and is ruled by ...}
{an Ancient of Days}{0}
{three Recents of Days}{0}
{one of the Seven Master Spirits}{0}
{Creator Son and Creative Mother Spirit}{0}
{a System Sovereign}{1}
{three Vorondadek Sons, the Most Highs}{0}
\qstop

\qstart{Each constellation has an architectural sphere as its headquarters and is ruled by ...}
{Constellation Sovereign}{0}
{Ancients of Days}{0}
{Recents of Days}{0}
{Seven Master Spirits}{0}
{three Vorondadek Sons, the Most Highs}{1}
{Creator Son and Creative Mother Spirit}{0}
\qstop

\qstart{Who serves as an ambassador of the Paradise Trinity and an observer on each constellation?}
{three Faithfuls of Days}{0}
{a Faithful of Days}{1}
{a Recent of Days}{0}
{seven Recents of Days}{0}
\qstop

\qstart{Each local universe has a magnificent architectural sphere as its headquarters and is ruled by ...}
{a Union of Days}{0}
{a Recent of Days}{0}
{one of the Seven Master Spirits}{0}
{a Paradise Creator Son}{1}
{three Vorondadek Sons, the Most Highs}{0}
\qstop

\qstart{Who serves as a representative of the Paradise Trinity on each local universe?}
{three Faithfuls of Days}{0}
{a Recent of Days}{0}
{seven Recents of Days}{0}
{a Faithful of Days}{0}
{a Union of Days}{1}
\qstop

\qstart{How many local universes constitute a minor sector?}
{10}{0}
{24}{0}
{100000}{0}
{70}{0}
{100}{1}
\qstop

\qstart{How many inhabited worlds can there be in a minor sector?}
{1 billion}{1}
{10 billion}{0}
{100 million}{0}
{1 trillion}{0}
{700 million}{0}
\qstop

\qstart{Each minor sector has a wonderful architectural sphere as its headquarters and is ruled by ...}
{Paradise Creator Son}{0}
{three Unions of Days}{0}
{three Recents of Days}{1}
{one of the Seven Master Spirits}{0}
{three Vorondadek Sons, the Most Highs}{0}
\qstop

\qstart{How many minor sectors constitute a major sector?}
{10}{0}
{24}{0}
{100000}{0}
{70}{0}
{100}{1}
\qstop

\qstart{How many inhabited worlds can there be in a major sector?}
{1 billion}{0}
{1 trillion}{0}
{100 billion}{1}
{700 million}{0}
{100 million}{0}
\qstop

\qstart{Each major sector has a superb architectural sphere as its headquarters and is ruled by ...}
{Paradise Creator Son}{0}
{three Unions of Days}{0}
{three Recents of Days}{0}
{three Perfections of Days}{1}
{three Vorondadek Sons, the Most Highs}{0}
\qstop

\qstart{Who serves as a representative of the Paradise Trinity on each minor sector?}
{a Union of Days}{0}
{a Faithful of Days}{0}
{a Recent of Days}{0}
{a Perfection of Days}{0}
{no one, because minor sectors are ruled by three Recents of Days, the Supreme Trinity Personalities}{1}
\qstop

\qstart{Who serves as a representative of the Paradise Trinity on each major sector?}
{a Union of Days}{0}
{a Faithful of Days}{0}
{a Recent of Days}{0}
{a Perfection of Days}{0}
{no one, because major sectors are ruled by three Perfections of Days, the Supreme Trinity Personalities}{1}
\qstop

\qstart{How many major sectors constitute a superuniverse?}
{100}{0}
{24}{0}
{100000}{0}
{70}{0}
{10}{1}
\qstop

\qstart{Each superuniverse has an enormous and glorious architectural sphere as its headquarters and is ruled by ...}
{Paradise Creator Son}{0}
{three Unions of Days}{0}
{three Recents of Days}{0}
{three Perfections of Days}{0}
{three Ancients of Days}{1}
{three Vorondadek Sons, the Most Highs}{0}
\qstop

\qstart{How many inhabited worlds can there be in a superuniverse?}
{100 billion}{0}
{1 billion}{0}
{1 trillion}{1}
{100 trillion}{0}
{700 billion}{0}
\qstop

\qstart{Is the Milky Way galaxy related to the superuniverse of Orvonton in any way?}
{no, Milky Way is just an illusion of materialistic so-called ``scientists''}{0}
{yes, Milky Way represents the central nucleus of Orvonton}{1}
{no, they are two distinct and unrelated astronomical objects}{0}
\qstop

\qstart{How many of the 10 major sectors of Orvonton have been roughly identified by Urantian astronomers?}
{all 10}{0}
{7}{0}
{8}{1}
{1}{0}
{4}{0}
{6}{0}
{3}{0}
\qstop

\qstart{Where is the rotational centre of our minor sector situated?}
{in the star cloud of Sagittarius}{1}
{in the star cluster M5 of Serpens Caput}{0}
{in the star cluster M13 of Hercules}{0}
{in the star cluster M71 of Sagitta}{0}
{in the star cluster NGC 5139 (Omega Centauri)}{0}
\qstop

\qstart{Which of these revolutionary movements does our planet Urantia participate in?}
{The revolution of Urantia around its sun}{1}
{The circuit of our solar system about the nucleus of the former Andronover nebula}{1}
{The rotation of the Andronover stellar family and the associated clusters about the composite rotation-gravity center of the star cloud of Nebadon}{1}
{The swing of the local star cloud of Nebadon and its associated creations around the Sagittarius centre of their minor sector}{1}
{The rotation of the one hundred minor sectors, including Sagittarius, about their major sector}{1}
{The whirl of the ten major sectors, the so-called star drifts, about the Uversa headquarters of Orvonton}{1}
{The movement of Orvonton and six associated superuniverses around Paradise and Havona, the counterclockwise processional of the superuniverse space level}{1}
\qstop

\qstart{Which of these motions are genetic, i.e. inherent in their origin?}
{The revolution of Urantia around its sun}{1}
{The circuit of our solar system about the nucleus of the former Andronover nebula}{1}
{The rotation of the Andronover stellar family and the associated clusters about the composite rotation-gravity center of the star cloud of Nebadon}{0}
{The swing of the local star cloud of Nebadon and its associated creations around the Sagittarius centre of their minor sector}{0}
{The rotation of the one hundred minor sectors, including Sagittarius, about their major sector}{0}
{The whirl of the ten major sectors, the so-called star drifts, about the Uversa headquarters of Orvonton}{0}
{The movement of Orvonton and six associated superuniverses around Paradise and Havona, the counterclockwise processional of the superuniverse space level}{1}
\qstop

\qstart{Which of these motions are composite, i.e. partly produced by the intelligent and purposeful action of the Paradise force organizers?}
{The revolution of Urantia around its sun}{0}
{The circuit of our solar system about the nucleus of the former Andronover nebula}{0}
{The rotation of the Andronover stellar family and the associated clusters about the composite rotation-gravity center of the star cloud of Nebadon}{1}
{The swing of the local star cloud of Nebadon and its associated creations around the Sagittarius centre of their minor sector}{1}
{The rotation of the one hundred minor sectors, including Sagittarius, about their major sector}{1}
{The whirl of the ten major sectors, the so-called star drifts, about the Uversa headquarters of Orvonton}{1}
{The movement of Orvonton and six associated superuniverses around Paradise and Havona, the counterclockwise processional of the superuniverse space level}{0}
\qstop

\qstart{How many architectural worlds there would be in the seven superuniverses if all the projected local universes and their component parts were established?}
{453,313,764,407}{1}
{500 billion}{0}
{7 trillion}{0}
{7 billion}{0}
{5 billion}{0}
\qstop

\qstart{How many inhabited planets constitute a system?}
{1024}{0}
{1000}{1}
{500}{0}
{777}{0}
{1000000}{0}
\qstop

\qstart{How many systems constitute a constellation?}
{10}{0}
{24}{0}
{100000}{0}
{100}{1}
{70}{0}
\qstop

\qstart{How many inhabited worlds can there be in a single constellation?}
{1000}{0}
{1000000}{0}
{100000}{1}
{777}{0}
\qstop

\qstart{How many constellations constitute a local universe?}
{10}{0}
{24}{0}
{100}{1}
{100000}{0}
{70}{0}
\qstop

\qstart{How many inhabited worlds can there be in a local universe?}
{100000}{0}
{1000}{0}
{10000000}{1}
{777777}{0}
{700000}{0}
\qstop

\qstart{How many stars are there in the superuniverse of Orvonton?}
{70 trillion}{0}
{10 trillion}{1}
{1 trillion}{0}
{700 million}{0}
{70 million}{0}
\qstop

\qstart{How many planets in our solar system are at present suited to harbour life?}
{one (Urantia)}{0}
{two}{0}
{three}{1}
{four}{0}
{five}{0}
{six}{0}
{seven}{0}
{eight}{0}
{nine}{0}
\qstop

\qstart{How many of the cool planets in our superuniverse are habitable by beings of our order?}
{fewer than 1 in 5}{0}
{fewer than 1 in 10}{0}
{fewer than 1 in 40}{1}
{fewer than 1 in 100}{0}
{fewer than 1 in 1,000}{0}
{fewer than 1 in 1,000,000}{0}
\qstop

\qstart{Which of these space bodies have had an evolutionary origin?}
{The dark islands of space}{1}
{The suns}{1}
{Comets, meteors, and planetesimals}{1}
{Planets (including inhabited)}{1}
{Architectural spheres}{0}
\qstop

\qstart{Are there stars which emit light not accompanied by heat?}
{yes}{1}
{no}{0}
\qstop

\qstart{Which of these is the capital of our local system?}
{Salvington}{0}
{Edentia}{0}
{Uversa}{0}
{Jerusem}{1}
\qstop

\qstart{Which of these is the headquarters of our constellation?}
{Salvington}{0}
{Edentia}{1}
{Uversa}{0}
{Jerusem}{0}
\qstop

\qpaper{16}{The Seven Master Spirits}

\qstart{Which of these are the realms with which the Seven Master Spirits have nothing whatever to do?}
{The bestowal and ministry of the Thought Adjusters}{1}
{The functions of the Unqualified Absolute}{1}
{The reflectivity mechanism of the local universes and the superuniverse}{0}
{The bestowal of the Spirit of Truth}{0}
{The bestowal of the Holy Spirit}{0}
{The life-initiation procedures of the local universe Life Carriers}{0}
{The life activations of the adjutant mind-spirits bestowed upon the worlds by a local universe Creative Spirit}{0}
\qstop

\qstart{Is it true that only a God-knowing individual can truly love another as himself?}
{yes}{1}
{no}{0}
\qstop

\qstart{Can objective unselfish social consciousness be other than religious consciousness?}
{no}{1}
{yes}{0}
\qstop

\qstart{Why are manmade civilizations unstable?}
{because they are not cosmic, not innate in the cosmic-mind endowment of the individuals of the races}{1}
{because Satan is constantly trying to destabilize them}{0}
{because God is destabilizing them}{0}
{because of the constant struggle between good and evil}{0}
\qstop

\qstart{Which of these are contributing to the stability of civilization?}
{science}{1}
{morality}{1}
{religion}{1}
{commerce}{0}
{wars}{0}
\qstop

\qstart{What is the total number of associative possibilities of three Deities?}
{7}{1}
{9}{0}
{3}{0}
{12}{0}
{24}{0}
{$\infty$}{0}
\qstop

\qstart{Which of these are \bibemph{not} absonite beings?}
{Architects of the Master Universe}{0}
{Primary Master Force Organizers}{0}
{Transcendental Recorders}{0}
{Seven Master Spirits}{1}
\qstop

\qpaper{17}{The Seven Supreme Spirit Groups}

\qstart{What is the domain of work of the Seven Spirits of the Circuits?}
{Paradise}{0}
{Havona}{1}
{seven superuniverses}{0}
{four outer space levels}{0}
{master universe}{0}
{grand universe}{0}
\qstop

\qstart{Do Thought Adjusters participate in the operation of the universal reflectivity system?}
{yes}{0}
{no}{1}
\qstop

\qstart{Is the reflective focus of each superuniverse identical with the point of spiritual polarity?}
{yes}{0}
{no}{1}
\qstop

\qstart{Are all Father fragments cognizant of the transactions of the universal reflectivity system?}
{yes}{1}
{no}{0}
\qstop

\qstart{What is the space range limit of the extra-Paradise reflectivity service in the present universe age?}
{periphery of the seven superuniverses}{1}
{periphery of the first outer space level}{0}
{periphery of the fourth outer space level}{0}
{periphery of Havona}{0}
\qstop

\qstart{How many of the 50 Reflective Spirits are of Paradise Trinity origin?}
{all 50}{0}
{49}{1}
{7}{0}
{14}{0}
{none of them}{0}
\qstop

\qstart{How many Reflective Image Aids are there?}
{7}{0}
{3}{0}
{49}{1}
{50}{0}
{144000}{0}
\qstop

\qstart{How many Reflective Image Aids are on the headquarters of each superuniverse?}
{7}{1}
{3}{0}
{49}{0}
{50}{0}
{12000}{0}
{1}{0}
\qstop

\qstart{Who are the creators of the Reflective Image Aids?}
{Reflective Spirits}{1}
{Paradise Trinity}{0}
{Paradise Trinity in functional liaison with the Deity Absolute}{0}
{Paradise Trinity in unrevealed association with the Unqualified Absolute}{0}
{The Father Reflective Image Aid \#1}{0}
\qstop

\qstart{Do the Reflective Image Aids possess the attribute of reflectivity, like their creators — the Reflective Spirits?}
{yes}{0}
{no}{1}
\qstop

\qstart{Do the Reflective Image Aids function directly in connection with the training worlds of ascending mortals?}
{yes}{0}
{no}{1}
\qstop

\qstart{Will the mortals of Urantia come in personal contact with the Reflective Image Aids during the sojourn in the Uversa schools?}
{yes}{0}
{no}{1}
\qstop

\qstart{Do ascending mortals, as a class, contact intimately with reflectivity?}
{yes}{0}
{no}{1}
\qstop

\qstart{Are ascendant pilgrims from evoluionary spheres able to hold personal communion with the Seven Spirits of the Circuits?}
{yes}{0}
{no}{1}
\qstop

\qstart{Which of these divine personalities were created by the Supreme Being in functional liaison with the Deity Absolute?}
{Majeston}{1}
{Seven Executive Spirits}{0}
{Trinity Teacher Sons}{0}
{Supreme Circuit Supervisor}{0}
{Trinitized Secrets of Supremacy}{0}
\qstop

\qstart{Which of these are the revealed phases of the career of a local universe Mother Spirit?}
{Initial Paradise Differentiation}{1}
{Preliminary Creatorship Training}{1}
{The Stage of Physical Creation}{1}
{The Life-Creation Era}{1}
{The Postbestowal Ages}{1}
{The Ages of Light and Life}{1}
\qstop

\qpaper{18}{The Supreme Trinity Personalities}

\qstart{Which of these are known as the Supreme Trinity Personalities?}
{Trinitized Secrets of Supremacy}{1}
{Eternals of Days}{1}
{Ancients of Days}{1}
{Perfections of Days}{1}
{Recents of Days}{1}
{Unions of Days}{1}
{Faithfuls of Days}{1}
{Wise of Days}{0}
{Mighty of Days}{0}
\qstop

\qstart{The number of Supreme Trinity Personalities is ...}
{increasing}{0}
{fixed}{1}
{decreasing}{0}
\qstop

\qstart{How many Trinitized Secrets of Supremacy supervise each of the seven sacred worlds of the Father?}
{10}{1}
{7}{0}
{3}{0}
{1}{0}
{70}{0}
\qstop

\qstart{How many Eternals of Days are in existence?}
{1 billion}{1}
{7 billion}{0}
{70}{0}
{21}{0}
{7}{0}
\qstop

\qstart{How many Eternals of Days rule each of one billion perfect worlds of Havona?}
{1}{1}
{3}{0}
{7}{0}
{10}{0}
\qstop

\qstart{How many Trinitized Secrets of Supremacy are in existence?}
{70}{1}
{7 billion}{0}
{7}{0}
{21}{0}
{77}{0}
{1 billion}{0}
\qstop

\qstart{Are there any records of the origin of the Eternals of Days in existence?}
{yes}{0}
{no}{1}
\qstop

\qstart{Are there any records of the origin of the Trinitized Secrets of Supremacy in existence?}
{yes}{0}
{no}{1}
\qstop

\qstart{Are the Eternals of Days visible to all will creatures dwelling in their domains?}
{yes}{1}
{no}{0}
\qstop

\qstart{Can an Eternal of Days be absent from his Havona sphere?}
{yes}{1}
{no}{0}
\qstop

\qstart{Who directs the Havona sphere during the absence of its Eternal of Days?}
{a Trinity Teacher Son}{1}
{an Avonal Son}{0}
{a Daynal Son}{0}
{a Michael Son}{0}
{an Ancient of Days}{0}
\qstop

\qstart{Are there any records of the origin (trinitization) of the Ancients of Days in existence?}
{yes, on Paradise}{1}
{no}{0}
\qstop

\qstart{How many Perfections of Days are there in existence?}
{21}{0}
{210}{1}
{7}{0}
{70}{0}
{1 billion}{0}
{7 billion}{0}
\qstop

\qstart{Is it necessary that all three Perfections of Days be present on the capital of their major sector?}
{yes}{0}
{no, one may be absent}{1}
{no, one or two may be absent}{0}
{no, all three may be absent}{0}
\qstop

\qstart{Will the mortals of Urantia see the Perfections of Days when they advance to the headquarters of Splandon?}
{yes}{1}
{no}{0}
\qstop

\qstart{How many of the ten major sectors of our superuniverse will the mortals of Urantia pass during their ascent?}
{only one, Splandon}{0}
{all ten}{1}
{three}{0}
{four}{0}
{two}{0}
\qstop

\qstart{How many of the Orvonton Perfections of Days will the mortals of Urantia see before they reach Uversa?}
{all 30}{1}
{3}{0}
{7}{0}
{70}{0}
{1}{0}
\qstop

\qstart{How many Recents of Days are there in existence?}
{21000}{1}
{210}{0}
{7}{0}
{70}{0}
{1 billion}{0}
{21}{0}
\qstop

\qstart{How many Unions of Days are there in existence?}
{700000}{1}
{21000}{0}
{700}{0}
{70}{0}
{1 billion}{0}
{21}{0}
\qstop

\qstart{How many Faithfuls of Days are there in existence?}
{70000000}{1}
{21000}{0}
{7000000}{0}
{70}{0}
{1 billion}{0}
{21}{0}
\qstop

\qstart{How many of the three Recents of Days are always on duty at the headquarters of their minor sector?}
{all three}{0}
{at least one}{1}
{at least two}{0}
\qstop

\qstart{How many minor sectors will the mortals of Urantia have to traverse on their ascent to Uversa?}
{only one, Ensa}{1}
{all 100 minor sectors of their major sector of Splandon}{0}
{all 1000 minor sectors of their suoeruniverse of Orvonton}{0}
\qstop

\qpaper{19}{The Co\hyp{}ordinate Trinity\hyp{}Origin Beings}

\qstart{Trinity Teacher Sons are devoted to...}
{conscious enlightenment of universe creatures}{1}
{subconscious enlightenment of universe creatures}{0}
{superconscious enlightenment of universe creatures}{0}
\qstop

\qstart{Inspired Trinity Spirits are devoted to...}
{conscious enlightenment of universe creatures}{0}
{subconscious enlightenment of universe creatures}{0}
{superconscious enlightenment of universe creatures}{1}
\qstop

\qstart{How many Universal Censors are there in existence?}
{8 billion}{1}
{7 billion}{0}
{1 billion}{0}
{800000}{0}
{700000}{0}
\qstop

\qstart{How many Universal Censors are assigned to each of the seven superuniverses?}
{1 billion}{1}
{3}{0}
{3 billion}{0}
{1}{0}
\qstop

\qstart{How many Universal Censors are assigned to the central universe?}
{1 billion}{1}
{3}{0}
{3 billion}{0}
{1}{0}
{none}{0}
\qstop

\qstart{How many Perfectors of Wisdom are there in existence?}
{7 billion}{1}
{8 billion}{0}
{1 billion}{0}
{800000}{0}
{700000}{0}
\qstop

\qstart{How many Perfectors of Wisdom are assigned to each of the seven superuniverses?}
{1 billion}{1}
{3}{0}
{3 billion}{0}
{1}{0}
\qstop

\qstart{How many Perfectors of Wisdom are assigned to the central universe?}
{1 billion}{0}
{3}{0}
{3 billion}{0}
{1}{0}
{none}{1}
\qstop

\qstart{How many Universal Censors are commissioned on each of the billion worlds of the central universe?}
{1}{1}
{3}{0}
{7}{0}
{10}{0}
{1000}{0}
{21}{0}
\qstop

\qstart{How many Divine Counsellors are there in existence?}
{21 billion}{1}
{8 billion}{0}
{1 billion}{0}
{800000}{0}
{700000}{0}
\qstop

\qstart{How many Divine Counsellors are assigned to each of the seven superuniverses?}
{3 billion}{1}
{3}{0}
{1 billion}{0}
{1}{0}
\qstop

\qstart{Which of these are known as the Stationary Sons of the Trinity?}
{Universal Censors}{1}
{Perfectors of Wisdom}{1}
{Divine Counsellors}{1}
{Ancients of Days}{1}
{Trinity Teacher Sons}{0}
{Inspired Trinity Spirits}{0}
{Trinitized Custodians}{0}
{Trinitized Sons of Perfectiom}{0}
\qstop

\qstart{How many Stationary Sons of the Trinity are there in existence?}
{over 37 billion}{1}
{about 1 billion}{0}
{about 7 billion}{0}
{over 1 trillion}{0}
{over 70 trillion}{0}
\qstop

\qpaper{20}{The Paradise Sons of God}

\qstart{When does a bestowal Son begin his planetary mission to enlighten the minds and to inspire the souls of his brethren in the flesh?}
{after perfect attunement with his indwelling Thought Adjuster}{1}
{after reaching the age of 30}{0}
{after receiving explicit instruction from his superiors}{0}
{at the earliest opportunity to do so, no restrictions}{0}
\qstop

\qstart{For how long do the Trinity Teachers Sons usually remain on the planet of their visitation?}
{1000 years}{1}
{100 years}{0}
{40 years}{0}
{40 days}{0}
{1 year}{0}
{7 days}{0}
\qstop

\qstart{Are Trinity Teacher Sons (Daynals) visible to mortal inhabitants of the planet of their visitation?}
{yes}{0}
{no}{1}
\qstop

\qstart{Which orders of the Paradise bestowal Sons are exempt from the restriction prohibiting them to beget children on the worlds of their bestowal?}
{Michaels}{0}
{Daynals}{0}
{Avonals}{0}
{none}{1}
\qstop

\qstart{Which of these orders of the Paradise Sons re-appear on the third day after they enter the portals of death?}
{Creator Sons}{1}
{Magisterial Sons}{1}
{Trinity Teacher Sons}{0}
\qstop

\qstart{How many Magisterial Sons are there in the grand universe?}
{1 billion}{1}
{7 billion}{0}
{21 billion}{0}
{7000}{0}
{7}{0}
\qstop

\qpaper{21}{The Paradise Creator Sons}

\qpaper{22}{The Trinitized Sons of God}

\qstart{Which orders of personalities can aspire to become Trinitized Custodians?}
{ascendant mortals}{0}
{ascendant seraphim}{1}
{translated midway creatures}{1}
{Melchizedeks}{0}
{Havona natives}{0}
\qstop

\qstart{How many of Those without Name and Number are of record on Uversa?}
{777}{0}
{12 thousand}{0}
{1 million}{0}
{100 million}{1}
\qstop

\qstart{Which of these orders of personalities are known as the Trinity-Embraced Sons?}
{Mighty Messengers}{1}
{Those High in Authority}{1}
{Celestial Guardians}{1}
{Melchizedeks}{0}
{Vorondadek Sons}{0}
{Lanonandek Sons}{0}
{High Son Assistants}{1}
\qstop

\qstart{Are there any pilgrims from the local universe of Nebadon among the Mighty Messengers?}
{no, the universe of Nebadon is too young}{0}
{yes}{1}
\qstop

\qstart{How many Mighty Messengers are commissioned on Uversa?}
{21 thousand}{0}
{144 thousand}{0}
{7 million}{0}
{1 billion}{0}
{1 trillion}{1}
\qstop

\qstart{Does the number of Mighty Messengers differ from superuniverse to superuniverse?}
{yes}{0}
{no}{1}
\qstop

\qstart{How many Trinitized Ambassadors are registered on Uversa?}
{500 thousand}{0}
{1 million}{0}
{500 million}{1}
{1 billion}{0}
{7 billion}{0}
{144 billion}{0}
{1 trillion}{0}
\qstop

\qstart{Who issues the orders authorizing the trinitization attempt by the ascendant Adjuster-fused mortal-finaliters?}
{Master Spirit Number Seven}{1}
{Master Spirit Number One}{0}
{Master Spirit of the superuniverse of the creature's origin}{0}
{Ancients of Days of the superuniverse of the creature's origin}{0}
{Universal Father}{0}
{Infinite Spirit}{0}
{Eternal Son}{0}
\qstop

\qstart{How many Trinitized Custodians are in service in the superuniverse of Orvonton?}
{144 thousand}{0}
{1 thousand}{0}
{1 million}{0}
{10 million}{1}
{1 billion}{0}
{1 trillion}{0}
\qstop

\qstart{Which of these beings can aspire to become Those High in Authority?}
{Adjuster-fused beings of mortal origin}{1}
{ascendant seraphim}{0}
{translated midway creatures}{0}
{any order of being}{0}
{only Trinity-origin beings}{0}
\qstop

\qstart{How many of Those High in Authority are commissioned in the superuniverse of Orvonton?}
{1 thousand}{0}
{1 million}{0}
{1 billion}{0}
{7 billion}{0}
{>10 billion}{1}
{1 trillion}{0}
\qstop

\qpaper{23}{The Solitary Messengers}

\qstart{What is the maximum velocity of an enseraphimed being?}
{36,000 km/s}{0}
{100,000 km/s}{0}
{299,792 km/s}{0}
{899,366 km/s}{1}
{1,000,000 km/s}{0}
{unlimited}{0}
\qstop

\qpaper{24}{Higher Personalities of the Infinite Spirit}

\qstart{Do the Census Directors function on Paradise?}
{Yes, they keep track of all will creatures present on Paradise}{0}
{No, because on Paradise knowledge is inherent --- the Deities know all things}{1}
{Yes, they keep track of all will creatures present on Paradise and Havona worlds}{0}
\qstop

\qstart{Do the Census Directors function in Havona?}
{yes}{1}
{no}{0}
\qstop

\qstart{How many Census Directors are stationed in Havona?}
{seven}{1}
{twelve}{0}
{ten}{0}
{one billion}{0}
{seven billion}{0}
\qstop

\qstart{Who or what is Malvorian?}
{Name of a geological era of Urantia}{0}
{Name of the first Graduate Guide}{1}
{Name of the Chief of the order of Graduate Guides}{1}
{Name of the first pilgrim of time who reached Havona}{0}
{Name of the Graduate Guide who accompanied the first pilgrim of time who reached Havona}{1}
\qstop

\qstart{Which of these was the first pilgrim of time who attained Havona?}
{Orvonon}{0}
{Onamonalonton}{0}
{Onagar}{0}
{Moses}{0}
{Orlandof}{0}
{Porshunta}{0}
{Grandfanda}{1}
{Jesus of Nazareth}{0}
\qstop

\qstart{From which superuniverse was the first pilgrim of time?}
{number one}{1}
{number two}{0}
{number three}{0}
{number four}{0}
{number five}{0}
{number six}{0}
{number seven}{0}
\qstop

\qstart{What was the native planet of Grandfanda?}
{planet 1, system 1, constellation 1, local universe 1, superuniverse 1}{0}
{planet 341, system 84, constellation 62, local universe 1,131, superuniverse 1}{1}
{planet 40, system 24, constellation 299, local universe 3,123, superuniverse 1}{0}
{planet 340, system 4, constellation 2, local universe 1,312, superuniverse 2}{0}
{planet 12, system 11, constellation 85, local universe 17, superuniverse 7}{0}
{Mars}{0}
{Venus}{0}
{Urantia}{0}
\qstop

\qstart{Which of these beings are endowed with antigravity?}
{Solitary Messengers}{1}
{Census Directors}{1}
{Universe Circuit Supervisors}{1}
{Associate Inspectors}{0}
{Supreme Power Centers}{1}
{Personal Aids of the Infinite Spirit}{1}
\qstop

\qstart{Does the Infinite Spirit transmit the power of antigravity to other personalities?}
{yes}{1}
{no}{0}
\qstop

\qstart{When do the Census Directors register the existence of a new will creature?}
{at the age of 5 years}{0}
{at the first act of will}{1}
{at the age of 7 years}{0}
{at birth}{0}
{at conception}{0}
{just before death}{0}
\qstop

\qstart{Do the Census Directors register an act of partial emergence of will in the higher animals?}
{yes}{0}
{no}{1}
\qstop

\qstart{Who is the chief of all Orvonton Census Directors?}
{Usatia}{1}
{Univitatia}{0}
{The Father Census Director}{0}
{Master Spirit Number Seven}{0}
{one of the Ancients of Days}{0}
\qstop

\qstart{Is Usatia directly attuned to the registration of intelligent will of all creatures in Orvonton?}
{yes}{0}
{no}{1}
\qstop

\qpaper{25}{The Messenger Hosts of Space}

\qstart{Which of these are classed among the Messenger Hosts of Space?}
{Havona Servitals}{1}
{Universal Conciliators}{1}
{Technical Advisers}{1}
{Graduate Guides}{0}
{Associate Inspectors}{0}
{Assigned Sentinels}{0}
{Personal Aids of the Infinite Spirit}{0}
\qstop

\qstart{How many Technical Advisers are registered on Uversa?}
{7 trillion}{0}
{61 trillion}{1}
{61 billion}{0}
{7 billion}{0}
{1 billion}{0}
{1 milliom}{0}
\qstop

\qstart{Can omniaphim Paradise Companions serve with the ascendant creatures from the seven superuniverses?}
{yes}{0}
{no}{1}
\qstop

\qpaper{26}{Ministering Spirits of the Central Universe}

\qstart{How many subjects do the ascendant mortals study during the ``elementary course'' on the seventh circle of Havona under the pilgrim helpers?}
{648}{0}
{9,200}{0}
{10,000}{0}
{100,000}{0}
{100,000,000}{0}
{1,234,800,000}{1}
{infinitely many}{0}
\qstop

\qstart{On which of the seven circles of Havona do the supremacy guides operate?}
{1}{0}
{2}{0}
{3}{0}
{4}{0}
{5}{0}
{6}{1}
{7}{0}
\qstop

\qstart{On which of the seven circles of Havona do the Trinity guides operate?}
{1}{0}
{2}{0}
{3}{0}
{4}{0}
{5}{1}
{6}{0}
{7}{0}
\qstop

\qstart{On which of the seven circles of Havona do the Son finders operate?}
{1}{0}
{2}{0}
{3}{0}
{4}{1}
{5}{0}
{6}{0}
{7}{0}
\qstop

\qstart{Do the candidates who failed the Deity adventure return to the superuniverse of their nativity?}
{yes}{0}
{no}{1}
\qstop

\qstart{On which of the seven circles of Havona do the Father guides operate?}
{1}{0}
{2}{0}
{3}{1}
{4}{0}
{5}{0}
{6}{0}
{7}{0}
\qstop

\qpaper{27}{Ministry of the Primary Supernaphim}

\qpaper{28}{Ministering Spirits of the Superuniverses}

\qpaper{29}{The Universe Power Directors}

\qstart{How many types of frandalanks can there be?}
{7}{0}
{24}{0}
{30}{1}
{777}{0}
\qstop

\qstart{What is an architectural world?}
{A made to order sphere independent of a sun thereby not visible from earth}{1}
{The world where the celestial architects live}{0}
{The world where celestial artisans live}{0}
{The world of the Master Architects}{0}
{The world with exquisite architecture}{0}
\qstop

\qstart{Does an architectural world have a sun, seasons, night and day, raging rivers, and oceans?}
{yes}{0}
{no}{1}
\qstop

\qpaper{30}{Personalities of the Grand Universe}

\qstart{Which of these are the seven stages of our grand universe ascension career?}
{Planetary mortals}{1}
{Sleeping survivors}{1}
{Mansion world students}{1}
{Morontia progressors}{1}
{Superuniverse wards}{1}
{Havona pilgrims}{1}
{Paradise arrivals}{1}
\qstop

\qstart{Which of the seven Supreme Spirit groups are classified as children of the Paradise Trinity?}
{The Seven Master Spirits}{1}
{The Seven Supreme Executives}{1}
{The Reflective Spirits}{1}
{The Reflective Image Aids}{0}
{The Seven Spirits of the Circuits}{0}
{The Local Universe Creative Spirits}{0}
{The Adjutant Mind-Spirits}{0}
\qstop

\qpaper{31}{The Corps of the Finality}

\qstart{How many Architects of the Master Universe are there?}
{1}{0}
{7}{0}
{12}{0}
{7000}{0}
{28,011}{1}
{28,012}{0}
\qstop

\qstart{At which eventuation level the quality of absonity equivalates to the level of the Universal and attains the value of the Absolute?}
{28,012\ts{th}}{1}
{28,011\ts{th}}{0}
{7,000\ts{th}}{0}
{7\ts{th}}{0}
{1\ts{st}}{0}
\qstop

\qpaper{32}{The Evolution of Local Universes}

\qstart{How far is Jerusem, the headquarters of Satania, from the physical centre of the superuniverse of Orvonton?}
{100,000 ly}{0}
{200,000 ly}{1}
{1 billion ly}{0}
{1 million ly}{0}
\qstop

\qstart{Which of these are our neighbouring local universes?}
{Avalon}{1}
{Henselon}{1}
{Sanselon}{1}
{Majeston}{0}
{Salvington}{0}
{Spironga}{0}
{Usatia}{0}
\qstop

\qstart{Why do most human beings die?}
{Because of the ``original sin'' of Adam and Eve}{0}
{Because it is appointed for all men to die once and then stand in judgement}{0}
{Because their bodies wear out eventually}{0}
{Because they fail to achieve the spirit level of the fusion with the indwelling Thought Adjuster}{1}
{Because of many diseases}{0}
{Because of some unrevealed mysterious reason}{0}
\qstop

\qstart{How far is the outermost system of inhabited worlds from the centre of the superuniverse of Orvonton?}
{51,000 ly}{0}
{100,000 ly}{0}
{250,000 ly}{1}
{1 million ly}{0}
{1 billion ly}{0}
\qstop

\qstart{Where was King Arthur's sword Excalibur (Caliburnus) forged?}
{Henselon}{0}
{Avalon}{1}
{Sanselon}{0}
{Portalon}{0}
{Wolvering}{0}
{Fanoving}{0}
{Alvoring}{0}
\qstop

\qstart{How many inhabited worlds are there in our local universe of Nebadon?}
{227}{0}
{606}{0}
{619}{0}
{666}{0}
{100,987}{0}
{3,840,101}{1}
{12,878,111}{0}
\qstop

\qpaper{33}{Administration of the Local Universe}

\qstart{What is the name of the Trinity Ambassador of our local universe of Nebadon?}
{Gabriel}{0}
{Michael}{0}
{Satanael}{0}
{Uriel}{0}
{Raphael}{0}
{Zachariel}{0}
{Barachiel}{0}
{Immanuel}{1}
\qstop

\qstart{Who adjudicates the problems of a local system?}
{The Most Highs}{1}
{The Ancients of Days}{0}
{The Creator Son}{0}
{Melchizedeks}{0}
\qstop

\qpaper{34}{The Local Universe Mother Spirit}

\qstart{Which of these has deprived human races of that superior type of physical nature which would have been more consonant with spiritual aspirations?}
{Lucifer rebellion}{0}
{Caligastia upheaval}{0}
{Adamic default}{1}
\qstop

\qstart{What does the Bible refer to when it talks about ``the seven spirits of God like lamps burning before the throne''?}
{seven Absolutes}{0}
{seven Master Spirits of the superuniverses}{0}
{seven adjutant mind-spirits}{1}
\qstop

\qstart{Are animals relevant to the intellectual and physical evolution of humans?}
{Yes, because of the experiential growth of the first five adjutant mind-spirits}{1}
{Not at all}{0}
{Not anymore}{0}
\qstop

\qstart{How many adjutant mind-spirits are there?}
{3}{0}
{4}{0}
{7}{1}
{10}{0}
{12}{0}
\qstop

\qstart{Which of these is \bibemph{not} one of the seven adjutant mind-spirits?}
{intuition}{0}
{understanding}{0}
{courage}{0}
{knowledge}{0}
{counsel}{0}
{worship}{0}
{wisdom}{0}
{intellect}{1}
\qstop

\qstart{How many adjutant mind-spirits are reachable by subhuman (animal) mind?}
{all 7}{0}
{5}{1}
{4}{0}
{1}{0}
{none}{0}
{3}{0}
\qstop

\qstart{Which of the adjutant mind-spirits can minister only to human or midwayer (super-animal) level of mind?}
{worship and wisdom}{1}
{intuition and understanding}{0}
{courage and counsel}{0}
{intuition and knowledge}{0}
\qstop

\qstart{Which of the adjutant mind-spirits makes the most extensive contact with nonteachable (subhuman) levels of mind?}
{intuition}{1}
{courage}{0}
{counsel}{0}
{understanding}{0}
\qstop

\qstart{Which adjutant mind-spirit is responsible for spontaneous association of ideas and co-ordination of acquired knowledge?}
{understanding}{1}
{intuition}{0}
{knowledge}{0}
{wisdom}{0}
\qstop

\qstart{Which adjutant mind-spirit is responsible for the ability of will creatures to harmonize with their fellows and the origin of the gregarious instinct among the more lowly creatures?}
{counsel}{1}
{intuition}{0}
{understanding}{0}
{worship}{0}
{knowledge}{0}
\qstop

\qstart{How many adjutant mind-spirits minister to midwayer as well as human types of mind?}
{all seven}{0}
{three}{0}
{two}{1}
{four}{0}
\qstop

\qstart{Which adjutant mind-spirits minister to midwayer minds?}
{worship and wisdom}{1}
{intuition and wisdom}{0}
{knowledge and understanding}{0}
{counsel and wisdom}{0}
\qstop

\qstart{Receptivity to which of the seven adjutant mind-spirits serves as a badge for spiritual-ascension candidacy of mortals?}
{wisdom}{0}
{knowledge}{0}
{worship}{1}
{courage}{0}
\qstop

\qpaper{35}{The Local Universe Sons of God}

\qstart{How many Lanonandek Sons are there in the local universe of Nebadon?}
{144}{0}
{7,000}{0}
{12,000}{0}
{1,000,000}{0}
{12,000,000}{1}
\qstop

\qstart{How many primary Lanonandek Sons are there in the local universe of Nebadon?}
{12,000}{0}
{22,363}{0}
{70,041}{0}
{270,005}{0}
{709,841}{1}
{1,720,025}{0}
\qstop

\qstart{How many secondary Lanonandek Sons are there in the local universe of Nebadon?}
{22,365}{0}
{709,841}{0}
{1,200,056}{0}
{8,720,025}{0}
{10,234,601}{1}
\qstop

\qstart{How many tertiary Lanonandek Sons are there in the local universe of Nebadon?}
{22,365}{0}
{1,055,558}{1}
{10,234,601}{0}
\qstop

\qstart{How many Magisterial Sons (Avonals) are there in the local universe of Nebadon?}
{1,062}{1}
{223,650}{0}
{1,023,460}{0}
{1 billion}{0}
\qstop

\qstart{How many Vorondadek Sons are there in the local universe of Nebadon?}
{12}{0}
{1024}{0}
{22,365}{0}
{144,000}{0}
{1 million}{1}
{1 billion}{0}
\qstop

\qpaper{36}{The Life Carriers}

\qstart{How many Life Carriers are there in the local universe of Nebadon?}
{144,000}{0}
{223,650}{0}
{10,234,601}{0}
{100 million}{1}
{1 billion}{0}
\qstop

\qstart{How many midsonite worlds are in each local system of the universe of Nebadon?}
{1}{1}
{2}{0}
{3}{0}
{7}{0}
{10}{0}
{12}{0}
{30}{0}
{619}{0}
\qstop

\qstart{Which of these beings initiate life on the midsonite worlds?}
{Life Carriers}{0}
{Melchizedeks}{1}
{Seraphim}{0}
{Supernaphim}{0}
{Solitary Messengers}{0}
{Creator Sons}{0}
{Material Sons and Daughters of God}{0}
\qstop

\qstart{Do midsoniters reproduce?}
{yes}{1}
{no}{0}
\qstop

\qstart{Do midsoniters reproduce after being enseraphimed?}
{yes}{0}
{no}{1}
\qstop

\qstart{What is the maximum length of time given to Life Carriers to establish life on a new world?}
{100,000 years}{0}
{500,000 years}{1}
{10 million years}{0}
{1 billion years}{0}
{4 billion years}{0}
\qstop

\qstart{Do the seven adjutant mind-spirits ever become personal?}
{no}{1}
{yes}{0}
\qstop

\qstart{Which number is inherent in the physical organization of energy and matter, but not in the spiritual?}
{10}{1}
{7}{0}
{12}{0}
{24}{0}
\qstop

\qstart{How many configurations (by inheritance carriers) of will creatures are there in Orvonton?}
{7}{0}
{12}{1}
{10}{0}
{Infinitely many}{0}
\qstop

\qpaper{37}{Personalities of the Local Universe}

\qstart{What is the keynote of the whole educational system of the Universe?}
{power augmented by knowledge}{0}
{character acquired by enlightened experience}{1}
{control of mind over energy and over weaker minds}{0}
{infinite diversity in infinite combinations}{0}
{equal opportunities for all races and types of creatures}{0}
\qstop

\qstart{What are abandonters doing at present?}
{administering the routine affairs of their world}{1}
{helping midwayers}{0}
{teaching morontia progressors}{0}
{tending the gardens of Edentia}{0}
\qstop

\qstart{What is the name of the Bright and Morning Star of our local universe of Nebadon?}
{Michael}{0}
{Gabriel}{1}
{Satanael}{0}
{Uriel}{0}
{Raphael}{0}
{Zachariel}{0}
{Barachiel}{0}
{Immanuel}{0}
\qstop

\qstart{How many Bright and Morning Stars are brought forth in each local universe?}
{1}{1}
{3}{0}
{7}{0}
{10}{0}
{24}{0}
\qstop

\qstart{How many architectural spheres are there in our local universe of Nebadon?}
{9,910}{0}
{11,255}{0}
{144,000}{0}
{647,591}{1}
{1,000,000}{0}
{10,000,000}{0}
\qstop

\qpaper{38}{Ministering Spirits of the Local Universe}

\qstart{What was the name of the seraphim that did not allow John Zebedee to worship him?}
{Salsatia}{0}
{Susatia}{0}
{Malavatia}{0}
{Loyalatia}{1}
{Uzziel}{0}
{Raphael}{0}
\qstop

\qpaper{39}{The Seraphic Hosts}

\qpaper{40}{The Ascending Sons of God}

\qpaper{41}{Physical Aspects of the Local Universe}

\qstart{For how long will our Sun continue to shine at its present efficiency?}
{100 million years}{0}
{5 billion years}{0}
{25 billion years}{1}
{unknown}{0}
{indefinitely}{0}
\qstop

\qstart{When do the Supreme Power Centres rest?}
{about 10\% of their time}{0}
{about 50\% of their time}{0}
{about 1\% of their time}{0}
{about 95\% of their time}{0}
{never, they are always on duty}{1}
\qstop

\qstart{Do the Supreme Power Centres have a sense of humour?}
{no, because they have no ascendant past to revert to and laugh at}{1}
{yes, but nobody understands their jokes}{0}
{yes, their jokes are the best in the grand universe}{0}
{unrevealed}{0}
\qstop

\qstart{Can the Supreme Power Centres function on the ordinary (evolutionary) suns or planets?}
{yes}{0}
{no}{1}
\qstop

\qstart{How many stars are in our local system of Satania?}
{2000+}{1}
{1000+}{0}
{100000}{0}
{1000000}{0}
\qstop

\qstart{What is the largest star in our universe?}
{$\alpha$ Piscis Austrini (Fomalhaut)}{0}
{$\alpha$ Centauri}{0}
{$\alpha$ Scorpii (Antares)}{1}
{$\tau$ Ceti}{0}
\qstop

\qpaper{42}{Energy --- Mind and Matter}

\qstart{Can solar heat or pressure convert ultimatons back into puissant energy?}
{yes}{0}
{no}{1}
\qstop

\qstart{Can ultimatonic energies sometimes exhibit antigravity behaviour?}
{yes}{1}
{no}{0}
\qstop

\qstart{What is the lowest density of matter-energy known in our local universe?}
{100 ultimatons in 16.4 cm\ts{3}}{1}
{10 ultimatons in 16.4 cm\ts{3}}{0}
{1 ultimaton in 16.4 cm\ts{3}}{0}
{0}{0}
\qstop

\qstart{How many ultimatons make one electron?}
{3}{0}
{10}{0}
{100}{1}
{300}{0}
{777}{0}
{1000}{0}
{70,000}{0}
\qstop

\qstart{By loss of one or more ultimatons how many modified forms of electron one may obtain?}
{100}{0}
{10}{1}
{7}{0}
{50}{0}
\qstop

\qpaper{43}{The Constellations}

\qstart{Who was the ``Most High'', which Melchizedek is said to be the priest of?}
{Yahweh, the Lord God of Israel}{0}
{Father Melchizedek}{0}
{Vorondadek observer}{1}
{Michael of Nebadon}{0}
\qstop

\qstart{At which point in our ascension will we be evolving from a morontia being (more material than spiritual) to the status of a true spirit?}
{From Mansion world no. 7}{0}
{From the Finaliter's world}{0}
{From the Salvington spheres}{1}
\qstop

\qpaper{44}{The Celestial Artisans}

\qstart{How many basic symbols are there in the alphabet of the local universe of Nebadon?}
{22}{0}
{24}{0}
{48}{1}
{70}{0}
{1000}{0}
{1024}{0}
{100,000}{0}
\qstop

\qstart{How many basic symbols are there in the alphabet of the superuniverse of Orvonton?}
{22}{0}
{24}{0}
{48}{0}
{70}{1}
{1000}{0}
{1024}{0}
{100,000}{0}
\qstop

\qpaper{45}{The Local System Administration}

\qstart{What type of being serves as a local System Sovereign?}
{Lanonandek Son}{1}
{Melchizedek}{0}
{Seraphim}{0}
{Omniaphim}{0}
{Seconaphim}{0}
{Ancient of Days}{0}
\qstop

\qstart{What is the registration number of our planet (Urantia) in the local system of Satania?}
{1}{0}
{777}{0}
{666}{0}
{606}{1}
{unknown}{0}
{37,011}{0}
\qstop

\qstart{How many inhabited worlds are in our local system of Satania?}
{1}{0}
{777}{0}
{666}{0}
{619}{1}
{unknown}{0}
{thousands}{0}
{millions}{0}
{37,001}{0}
\qstop

\qstart{Who is the current System Sovereign?}
{Lucifer}{0}
{Lanaforge}{1}
{Machiventa Melchizedek}{0}
{Jesus of Nazareth}{0}
{Enoch the Scribe}{0}
\qstop

\qstart{How many seats on the Urantia Advisory Council of 24 do Adam and Eve occupy?}
{two seats, \#9 and \#10}{1}
{one shared seat}{0}
{none, they are not members}{0}
\qstop

\qstart{How many seats of the Four and Twenty Counsellors are not permanently occupied?}
{8}{1}
{4}{0}
{0}{0}
{1}{0}
\qstop

\qpaper{46}{The Local System Headquarters}

\qstart{Chronoldek is...}
{the name for the upper deck on the ship that can travel through time}{0}
{a frandalank that registers time}{1}
{the name of a realm where time and space are inverted}{0}
\qstop

\qstart{Is the doctrine of human re\hyp{}incarnation true or false?}
{true}{0}
{false}{1}
\qstop

\qpaper{47}{The Seven Mansion Worlds}

\qstart{On which of the mansion worlds is the resurrection hall located?}
{\# 1}{1}
{\# 2}{0}
{\# 3}{0}
{\# 4}{0}
{\# 5}{0}
{\# 6}{0}
{\# 7}{0}
\qstop

\qpaper{48}{The Morontia Life}

\qstart{When do the 570 morontia transformations occur for the progressing ascenders?}
{8 in the system, 71 in the constellation, and 491 during the sojourn on the spheres of Salvington}{1}
{70 in the system, and 500 on the spheres of Salvington}{0}
{370 in the superuniverse levels and 200 on Paradise and Havona}{0}
\qstop

\qstart{How many morontia bodies are the ascending sons of God provided with on their progressive journey from material to spiritual life?}
{570}{1}
{1000}{0}
{300}{0}
{777}{0}
{3}{0}
{1}{0}
\qstop

\qstart{What are the morontia realms?}
{Liaison spheres between the material and spiritual levels of creature existence}{1}
{The morontia spheres are the transition phases of mortal ascension through the progression worlds of the local universe}{1}
{These worlds are architectural spheres and they have double the number of elements of the evolved planets}{1}
{These worlds have 100 forms of a unique energy organisation called morontia material}{1}
\qstop

\qstart{What are mansion worlds?}
{The 7 satellites of the Finaliter World (world number 1), with the resurrection halls being on satellite number 1}{1}
{The Home of the Father}{0}
{The Home of angels}{0}
\qstop

\qstart{What are morontia worlds?}
{56 progression worlds of a local universe through which mortals have to ascend, becoming more morontial with each translation}{1}
{In our local system of Satania, the morontia worlds are the 7 transitional worlds encircling Jerusem (the HQ of Satania), and the 7 satellites of each these worlds, totalling 56 worlds}{1}
{The worlds where Lucifer and Satan are incarcerated}{0}
\qstop

\qstart{Is the morontia form spiritual or material?}
{neither (it is an intermediate stage between them)}{1}
{spiritual}{0}
{material}{0}
{combination of both}{0}
\qstop

\qpaper{49}{The Inhabited Worlds}

\qpaper{50}{The Planetary Princes}

\qpaper{51}{The Planetary Adams}

\qstart{When is the slavery abolished on a normal evolutionary sphere?}
{upon arrival of Adam}{1}
{upon arrival of Planetary Prince}{0}
{in the age of Light and Life}{0}
{persists forever}{0}
\qstop

\qpaper{52}{Planetary Mortal Epochs}

\qstart{Why was Moses not permitted to ``go to the other side'' (i.e. be resurrected on the mansion world)?}
{because the fallen Planetary Prince Caligastia was contesting such a deliverance}{1}
{because he was a secret sinner}{0}
{because the resurrection hall on Mansonia One was not yet constructed}{0}
\qstop

\qstart{Since what event do the Urantia mortals may proceed directly to the morontia spheres after death?}
{Pentecost}{1}
{Jesus' birth}{0}
{Jesus' crucifixion}{0}
{Jesus' resurrection}{0}
{Jesus' baptism}{0}
\qstop

\qpaper{53}{The Lucifer Rebellion}

\qstart{How many inhabited worlds were in the local system of Satania at the time of Lucifer rebellion?}
{599}{0}
{606}{0}
{607}{1}
{612}{0}
{619}{0}
{666}{0}
\qstop

\qstart{Who was Lucifer at the time of the rebellion?}
{System Sovereign}{1}
{Planetary Prince}{0}
{Member of System Sovereign's Staff}{0}
{Free from assignment}{0}
\qstop

\qstart{When did the Lucifer rebellion occur in the system of Satania?}
{200,000 years ago}{1}
{300,000 years ago}{0}
{500,000 years ago}{0}
{1 million years ago}{0}
{6,000 years ago}{0}
\qstop

\qstart{Lucifer was a ...}
{Primary Lanonandek Son}{1}
{Secondary Lanonandek Son}{0}
{Melchizedek}{0}
{Seraphim}{0}
{Archangel}{0}
\qstop

\qstart{Satan was a...}
{Primary Lanonandek Son}{1}
{Secondary Lanonandek Son}{0}
{Melchizedek}{0}
{Seraphim}{0}
{Archangel}{0}
\qstop

\qstart{Who was the chief of the staff of Caligastia and the leader of the rebels?}
{Abaddon}{1}
{Beelzebub}{0}
{Satan}{0}
{Judas Iscariot}{0}
\qstop

\qstart{Who was the leader of the disloyal midway creatures?}
{Beelzebub}{1}
{Abaddon}{0}
{Satan}{0}
{Judas Iscariot}{0}
\qstop

\qstart{Caligastia was a..}
{Primary Lanonandek Son}{0}
{Secondary Lanonandek Son}{1}
{Melchizedek}{0}
{Seraphim}{0}
{Archangel}{0}
\qstop

\qstart{The dragon of the Revelation of John is symbolic of...}
{Abaddon}{1}
{Judas Iscariot}{0}
{Beelzebub}{1}
{Lucifer}{1}
{Satan}{1}
{Stalin}{0}
\qstop

\qstart{The fallen prince Caligastia is now...}
{freely roaming this planet}{1}
{in custody}{0}
{executed}{0}
\qstop

\qstart{Lucifer is now...}
{freely roaming the local system of Satania}{0}
{in custody}{1}
{executed}{0}
\qstop

\qstart{Satan is now...}
{freely roaming the local system of Satania}{0}
{in custody}{1}
{executed}{0}
\qstop

\qpaper{54}{Problems of the Lucifer Rebellion}

\qpaper{55}{The Spheres of Light and Life}

\qpaper{56}{Universal Unity}

\qstart{Did the Absolute (the three Absolutes as one in infinity) exist before the Trinity?}
{no}{1}
{yes}{0}
\qstop

\qpaper{57}{The Origin of Urantia}

\qstart{Our planet is known locally as...}
{the world of the cross}{1}
{the kingdom of the stupid}{0}
{the blue marble}{0}
{planet of the apes}{0}
{the world of Jesus Christ}{0}
{the little world with a big problem}{0}
\qstop

\qstart{How long ago was our Sun born?}
{6,000 years}{0}
{4.6 billion years}{0}
{6 billion years}{1}
{9 billion years}{0}
{10 billion years}{0}
\qstop

\qpaper{58}{Life Establishment on Urantia}

\qstart{What is the cause of earthquakes on our planet?}
{volcanoes}{0}
{God's wrath}{0}
{sliding and shifting of the solid outer crust}{1}
{angels}{0}
{evil spirits}{0}
{demons}{0}
{manmade technologies}{0}
\qstop

\qstart{When was the life implanted on our planet?}
{6000 years ago, on the third day of creation by God}{0}
{1 million years ago}{0}
{150 million years ago}{0}
{550 million years ago}{1}
{1 billion years ago}{0}
\qstop

\qstart{When did the transition from vegetable to animal life on our planet occur?}
{6000 years ago, on the fourth day of creation by God}{0}
{85 million years ago}{0}
{170 million years ago}{0}
{450 million years ago}{1}
{1 billion years ago}{0}
\qstop

\qstart{Does human mind depend on the brain capacity?}
{yes}{1}
{no}{0}
\qstop

\qstart{How do the new species arise?}
{as the result of the gradual accumulation of small variations}{0}
{suddenly, as full\hyp{}fledged and new orders of life}{1}
{by the direct act of Deity}{0}
\qstop

\qpaper{59}{The Marine\hyp{}Life Era on Urantia}

\qstart{When does the history of our planet officially begin?}
{1 billion years ago}{1}
{100 million years ago}{0}
{1 million years ago}{0}
{6000 years ago}{0}
\qstop

\qstart{Into how many geologic eras is the history of our planet divided?}
{3}{0}
{5}{1}
{7}{0}
{10}{0}
{12}{0}
\qstop

\qstart{When was the Archeozoic (prelife) era?}
{1 billion to 550 million years ago}{1}
{500 to 400 million years ago}{0}
{100 to 50 million years ago}{0}
\qstop

\qstart{When was the Proterozoic (life dawn) era?}
{10 to 5 million years ago}{0}
{400 to 300 million years ago}{0}
{550 to 400 million years ago}{1}
\qstop

\qstart{When was the Paleozoic (marine-life) era?}
{200 to 50 million years ago}{0}
{400 to 150 million years ago}{1}
{541 to 252 million years ago}{0}
\qstop

\qstart{When was the Mesozoic (early land-life) era?}
{10 to 5 million years ago}{0}
{50 to 10 million years ago}{0}
{150 to 50 million years ago}{1}
\qstop

\qstart{When was the Cenozoic (mammalian) era?}
{6000 years ago to the present}{0}
{5 milion years ago to the present}{0}
{50 million years ago to the present}{1}
{150 million years ago to the present}{0}
\qstop

\qstart{Into how many geologic ages is the Paleozoic era divided?}
{3}{0}
{5}{0}
{6}{1}
{7}{0}
{12}{0}
\qstop

\qstart{When was the Cambrian (trilobite) age, the first age of the Paleozoic era?}
{50 to 15 million years ago}{0}
{400 to 225 million years ago}{0}
{400 to 350 million years ago}{1}
{540 to 480 million years ago}{0}
\qstop

\qstart{When was the Ordovician (invertebrate-animal) age, the second age of the Paleozoic era?}
{50 to 25 million years ago}{0}
{485 to 443 million years ago}{0}
{350 to 300 million years ago}{1}
{410 to 100 million years ago}{0}
\qstop

\qstart{When was the Silurian (coral and brachiopod) age, the third age of the Paleozoic era?}
{145 to 130 million years ago}{0}
{300 to 270 million years ago}{1}
{300 to 100 million years ago}{0}
{440 to 400 million years ago}{0}
\qstop

\qstart{When was the Devonian (plant life, fishes) age, the fourth age of the Paleozoic era?}
{30 to 15 million years ago}{0}
{200 to 175 million years ago}{0}
{270 to 220 million years ago}{1}
{419 to 358 million years ago}{0}
\qstop

\qstart{When was the Carboniferous (fern forests, frogs) age, the fifth age of the Paleozoic era?}
{35 to 29 million years ago}{0}
{100 to 70 million years ago}{0}
{220 to 180 million years ago}{1}
{359 to 299 million years ago}{0}
\qstop

\qstart{When was the Permian (seed-plants; biologic tribulation) age, the sixth and the last age of the Paleozoic era?}
{25 to 11 million years ago}{0}
{110 to 60 million years ago}{0}
{170 to 150 million years ago}{1}
{290 to 250 million years ago}{0}
\qstop

\qstart{Into how many geologic ages is the Mezozoic (early land-life) era divided?}
{3}{1}
{4}{0}
{5}{0}
{7}{0}
\qstop

\qstart{When was the Triassic (early-reptilian) age, the first age of the Mezozoic era?}
{75 to 40 million years ago}{0}
{150 to 125 million years ago}{1}
{200 to 100 million years ago}{0}
{250 to 200 million years ago}{0}
\qstop

\qstart{When was the Jurassic (later-reptilian) age, the second age of the Mezozoic era?}
{60 to 35 million years ago}{0}
{150 to 50 million years ago}{0}
{125 to 100 million years ago}{1}
{200 to 145 million years ago}{0}
\qstop

\qstart{When was the Cretaceous (flowering plants, birds) age, the third and the last age of the Mezozoic era?}
{5 million years ago to the present}{0}
{80 to 25 million years ago}{0}
{100 to 50 million years ago}{1}
{145 to 66 million years ago}{0}
\qstop

\qpaper{60}{Urantia During the Early Land\hyp{}Life Era}

\qstart{When did the first (nonplacental) mammals appear on our planet?}
{\textasciitilde 135 million years ago}{1}
{\textasciitilde 200 million years ago}{0}
{\textasciitilde 100 million years ago}{0}
{\textasciitilde 50 million years ago}{0}
{\textasciitilde 10 million years ago}{0}
\qstop

\qstart{When did the first oaks appear on our planet?}
{1 million year ago}{0}
{65 million years ago}{1}
{276 million years ago}{0}
{500 million years ago}{0}
{1 billion year ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first birch trees appear on our planet?}
{65 million years ago}{1}
{1 million year ago}{0}
{1 billion year ago}{0}
{500 million years ago}{0}
{276 million years ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first beech trees appear on our planet?}
{65 million years ago}{1}
{1 million year ago}{0}
{1 billion year ago}{0}
{500 million years ago}{0}
{276 million years ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first walnut trees appear on our planet?}
{65 million years ago}{1}
{1 million year ago}{0}
{1 billion year ago}{0}
{500 million years ago}{0}
{276 million years ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first sycamore trees appear on our planet?}
{65 million years ago}{1}
{1 million year ago}{0}
{1 billion year ago}{0}
{500 million years ago}{0}
{276 million years ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first palm trees appear on our planet?}
{65 million years ago}{1}
{1 million year ago}{0}
{1 billion year ago}{0}
{500 million years ago}{0}
{276 million years ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first maple trees appear on our planet?}
{65 million years ago}{1}
{1 million year ago}{0}
{1 billion year ago}{0}
{500 million years ago}{0}
{276 million years ago}{0}
{1.5 billion years ago}{0}
{6000 years ago, on the 3rd day of creation}{0}
\qstop

\qstart{When did the first true birds appear on our planet?}
{55 million years ago}{1}
{125 million years ago}{0}
{2 billion years ago}{0}
{388 million years ago}{0}
{1 million years ago}{0}
{6000 years ago, on the 5\ts{th} day of creation}{0}
\qstop

\qpaper{61}{The Mammalian Era on Urantia}

\qstart{What are the present geologic age and period called?}
{Holocene period of Cenozoic era}{1}
{Pleistocene period of Cenozoic era}{0}
{Miocene period of Cenozoic era}{0}
{Jurassic period of Mesozoic era}{0}
{Devonian period of Paleozoic era}{0}
{Ordovician period of Paleozoic era}{0}
{Cretaceous period of Mesozoic era}{0}
{Oligocene period of Cenozoic era}{0}
\qstop

\qstart{Which animal is surpassed in intelligence only by human?}
{horse}{0}
{octopus}{0}
{elephant}{1}
{dog}{0}
{cat}{0}
{sabre-toothed tigre}{0}
{dolphin}{0}
{whale}{0}
{scorpion}{0}
\qstop

\qstart{When was the last great ice age terminated?}
{37,000 B.C.}{1}
{47,000 B.C.}{0}
{25,000 B.C.}{0}
{10,500 B.C.}{0}
\qstop

\qstart{When did the horse (as it now exists) evolve?}
{5 million years ago}{1}
{3 million years ago}{0}
{1 million years ago}{0}
{350,000 years ago}{0}
\qstop

\qstart{Where did the horse (as it now exists) evolve?}
{North America}{1}
{South America}{0}
{Africa}{0}
{Eurasia}{0}
{Australia}{0}
\qstop

\qstart{How old were Andon and Fonta (the first humans) when our world was registered as inhabited?}
{0 (i.e. registered at birth)}{0}
{5 years}{0}
{11 years}{1}
{16 years}{0}
{18 years}{0}
{30 years}{0}
{40 years}{0}
\qstop

\qpaper{62}{The Dawn Races of Early Man}

\qstart{When did the first human beings appear on our planet?}
{6,000 years ago}{0}
{35,000 years ago}{0}
{47,000 years ago}{0}
{470,000 years ago}{0}
{870,000 years ago}{0}
{1 million years ago}{1}
\qstop

\qstart{How did Andon and Fonta's parents die?}
{killed by gibbons}{1}
{killed by saber-toothed cat Smilodon}{0}
{died of old age}{0}
\qstop

\qstart{Is man an evolutionary descendant from apes?}
{no}{1}
{yes}{0}
\qstop

\qpaper{63}{The First Human Family}

\qstart{Which period of time is regarded as the golden age of primitive man when Adjusters and guardian seraphim first came in great numbers to Urantia?}
{In the days of Onagar nearly 981,389 years ago}{1}
{In the days of Andon \&\ Fonta 991,472 years ago}{0}
{When a better strain sprang from the Neanderthals, the Badonan tribes 500,000 ago}{0}
\qstop

\qstart{What names were bestowed upon the first human beings at the time of fusion?}
{Adam and Eve}{0}
{Cain and Abel}{0}
{Sonta\hyp{}an and Sonta\hyp{}en}{0}
{Andon and Fonta}{1}
{Abraham and Sarah}{0}
\qstop

\qstart{What decision of Andon and Fonta constituted their first response to the adjutant mind-spirit of wisdom?}
{worship God and him only}{0}
{marry}{0}
{flee home}{1}
{eat only vegetables}{0}
\qstop

\qstart{How many years did Andon and Fonta live?}
{42}{1}
{45}{0}
{120}{0}
{486}{0}
\qstop

\qstart{How did Andon and Fonta die?}
{rock fell on them during an earthquake}{1}
{drowned}{0}
{killed by gibbons}{0}
{ate poison mushrooms}{0}
\qstop

\qstart{Which present-day group of people resembles the early Andonites most?}
{negroes}{0}
{Eskimo}{1}
{native American indians}{0}
{Australian aborigenes}{0}
\qstop

\qstart{Which of the first humans responded to the influence of the adjutant mind-spirit of worship first?}
{Andon}{0}
{Fonta}{1}
\qstop

\qstart{Who were the Andonites?}
{Descendants of Andon \&\ Fonta}{1}
{Descendants of Adam \&\ Eve}{0}
{Descendants of the Orange race}{0}
{Descendants of Cain \&\ Remona}{0}
\qstop

\qpaper{64}{The Evolutionary Races of Colour}

\qstart{How long ago did the coloured races of humans appear?}
{1 million years}{0}
{500,000 years}{1}
{100,000 years}{0}
{46,000 years}{0}
{6,000 years ago}{0}
\qstop

\qstart{Which three of the evolutionary races are primary (superior intellectually and spiritually)?}
{red, yellow and blue}{1}
{red, green and blue}{0}
{orange, green and indigo}{0}
{orange, green and blue}{0}
\qstop

\qstart{Which three of the evolutionary races are secondary (inferior intellectually and spiritually)?}
{orange, green and indigo}{1}
{red, yellow and orange}{0}
{red, yellow and blue}{0}
{orange, yellow and indigo}{0}
\qstop

\qstart{Which of these was a great leader of green men 350,000 years ago?}
{Onagar}{0}
{Porshunta}{0}
{Fantad}{1}
{Sontad}{0}
\qstop

\qstart{Which of the coloured races of humans was preferred by Adamites for mating?}
{blue}{1}
{red}{0}
{yellow}{0}
{indigo}{0}
\qstop

\qstart{Which two of the coloured races of humans exhibited strains of giantism?}
{green and orange}{1}
{yellow and red}{0}
{blue and indigo}{0}
{blue and green}{0}
\qstop

\qstart{Which coloured races of our planet perished?}
{green and orange}{1}
{green and indigo}{0}
{blue and indigo}{0}
{red and yellow}{0}
\qstop


\qstart{Where is now the orange race of humans?}
{became extinct}{1}
{was taken by aliens}{0}
{never existed}{0}
\qstop

\qstart{Who was the great spiritual leader of the orange race about 300,000 years ago?}
{Porshunta}{1}
{Fantad}{0}
{Sontad}{0}
{Onamonalonton}{0}
{Onagar}{0}
\qstop

\qstart{Where was the headquarters of the orange race?}
{Armageddon}{1}
{Jerusalem}{0}
{Babylon}{0}
{Memphis}{0}
\qstop

\qstart{Who was the first of the yellow men to teach and lead his people in the worship of ``One Truth'' instead of many?}
{Singlangton}{1}
{Orlandof}{0}
{Porshunta}{0}
{Enoch}{0}
{Onamonalonton}{0}
\qstop

\qstart{When did Singlangton teach the yellow men of Urantia?}
{10,000 years ago}{0}
{100,000 years ago}{1}
{200,000 years ago}{0}
{212,000 years ago}{0}
{300,000 years ago}{0}
{370,000 years ago}{0}
\qstop

\qstart{Which of these was a great leader of American red race 65,000 years ago?}
{Onamonalonton}{1}
{Sontad}{0}
{Fantad}{0}
{Porshunta}{0}
{Onagar}{0}
\qstop

\qstart{When did Onamonalonton live on Urantia?}
{5,000 years ago}{0}
{25,000 years ago}{0}
{65,000 years ago}{1}
{85,000 years ago}{0}
{185,000 years ago}{0}
{200,000 years ago}{0}
\qstop

\qstart{What was Onamonalonton's age when he died?}
{46 years}{0}
{66 years}{0}
{96 years}{1}
{126 years}{0}
{156 years}{0}
{200 years}{0}
\qstop

\qstart{Where did Onamonalonton live?}
{Canada}{0}
{California}{1}
{Texas}{0}
{Mexico}{0}
\qstop

\qpaper{65}{The Overcontrol of Evolution}

\qpaper{66}{The Planetary Prince of Urantia}

\qstart{What was the name of the city of the Planetary Prince Caligastia?}
{Babylon the Great}{0}
{Akkad}{0}
{Dalamatia}{1}
{Jerusalem}{0}
{Eden}{0}
\qstop

\qstart{Where was the city of Dalamatia located?}
{Egypt}{0}
{Turkey}{0}
{Armenia}{0}
{Russia}{0}
{Africa}{0}
{Mesopotamia}{1}
{North America}{0}
{Australia}{0}
\qstop

\qstart{What or who is a fandor?}
{A kind of fish}{0}
{A kind of bird}{1}
{A kind of lizard}{0}
{A kind of snake}{0}
{A kind of angel}{0}
\qstop

\qstart{Which of these were employed as passenger birds?}
{ostriches}{0}
{fandors}{1}
{eagles}{0}
{pigeons}{0}
{crows}{0}
\qstop

\qstart{When did fandors become extinct?}
{30,000+ years ago}{1}
{50,000+ years ago}{0}
{150,000+ years ago}{0}
{250,000+ years ago}{0}
{1,000,000+ years ago}{0}
\qstop

\qstart{How long did it take to spread the news of the arrival of the Planetary Prince Caligastia around the world?}
{1000 years}{1}
{100 years}{0}
{500 years}{0}
{50,000 years}{0}
{25 years}{0}
\qstop

\qstart{What is the origin of the custom of nonflesh diet?}
{Caligastia 100}{1}
{Adam and Eve}{0}
{Moses}{0}
{the Egyptians}{0}
{the Babylonians}{0}
\qstop

\qstart{At what age did the graduates of Dalamatia school become eligible for marriage?}
{13}{0}
{15}{1}
{18}{0}
{20}{0}
{30}{0}
\qstop

\qpaper{67}{The Planetary Rebellion}

\qstart{Who was Nod?}
{A rebel member of Caligastia's staff}{1}
{A descendant of Andon \&\ Fonta}{0}
{A descendant of Adam}{0}
{Firstborn son of Cain \&\ Remona}{0}
\qstop

\qstart{Who were the Nodites?}
{The joint offspring of 44 of the modified Andonites and 60 corporeal members of Caligastia's staff who followed Nod into rebellion}{1}
{Followers of Cain who departed from the Garden of Eden for the Land of Nod and married Remona}{0}
{The joint offspring of Nod and his followers and the Adamites after the rebellion}{0}
\qstop

\qpaper{68}{The Dawn of Civilization}

\qstart{How many children in Madascar are destroyed because of being born on ``unlucky'' days?}
{none}{0}
{2\%}{0}
{15\%}{0}
{25\%}{1}
{50\%}{0}
{100\%}{0}
\qstop

\qstart{Which ancient people never had a taboo on twins?}
{Andonites}{1}
{red}{0}
{yellow}{0}
{orange}{0}
\qstop

\qpaper{69}{Primitive Human Institutions}

\qstart{When did the aborigines of Australia abolish slavery?}
{XV century}{0}
{XIX century}{0}
{XX century}{0}
{never had slaves}{1}
\qstop

\qstart{Who was the first slave on our planet?}
{woman}{1}
{black man}{0}
{white man}{0}
{yellow man}{0}
{red man}{0}
\qstop

\qpaper{70}{The Evolution of Human Government}

\qpaper{71}{Development of the State}

\qpaper{72}{Government on a Neighbouring Planet}

\qpaper{73}{The Garden of Eden}

\qstart{Who prepared the Garden of Eden before the arrival of Adam \&\ Eve?}
{volunteers}{1}
{hirelings}{0}
\qstop

\qstart{What happened to the first garden of Eden 4,000 years after Adam \&\ Eve left?}
{Sank in the Mediterranean}{1}
{Became desert land due to climate changes}{0}
{Became part of north Africa due to geological changes}{0}
{Was destroyed by the seraphim}{0}
{Was destroyed by Satan}{0}
\qstop

\qstart{What is the minimal size of Adamic family required for initiating racial uplifting of human races?}
{500,000 persons}{1}
{100 persons}{0}
{1,000,000 persons}{0}
{40 persons}{0}
\qstop

\qstart{Who sent the tree of life to Urantia?}
{Most Highs of Edentia}{1}
{Ancients of Days}{0}
{Melchizedeks}{0}
{Michael of Nebadon}{0}
{There was no such tree, it was a biblical myth}{0}
{Chief of Seraphim}{0}
\qstop

\qstart{Who brought the tree of life to Urantia?}
{Most Highs of Edentia}{0}
{Ancients of Days}{0}
{Melchizedeks}{1}
{Michael of Nebadon}{0}
{There was no such tree, it was a biblical myth}{0}
{Chief of Seraphim}{0}
\qstop

\qstart{Who sent the tree of knowledge of good and evil to Urantia?}
{Most Highs of Edentia}{0}
{Ancients of Days}{0}
{Melchizedeks}{0}
{Michael of Nebadon}{0}
{There was no such tree, it was a biblical myth}{1}
{Chief of Seraphim}{0}
{it grew locally}{0}
\qstop

\qstart{Who brought the tree of knowledge of good and evil to Urantia?}
{Most Highs of Edentia}{0}
{Ancients of Days}{0}
{Melchizedeks}{0}
{Michael of Nebadon}{0}
{There was no such tree, it was a biblical myth}{1}
{Chief of Seraphim}{0}
{it grew locally}{0}
\qstop


\qstart{Who guarded the tree of life in the garden of Eden after Adam and Eve left it?}
{seraphim with a sword}{0}
{cherubim with a flaming sword turning every way}{0}
{primary midwayers}{0}
{secondary midwayers}{0}
{no one}{1}
\qstop

\qstart{What happened to the tree of life after Nodites invaded Eden?}
{destroyed by fire}{1}
{chopped into pieces and swallowed}{0}
{ground to dust}{0}
{sold for thirty pieces of silver}{0}
\qstop

\qstart{What happened to the Nodites after they ate of the tree of life?}
{nothing}{1}
{it poisoned them}{0}
{lightning struck them dead}{0}
{they developed stomach cancer within 7 days}{0}
\qstop

\qstart{What does the Biblical expression ``eating of the tree of the knowledge of good and evil'' really mean?}
{literally eating of some forbidden tree, as the Bible says so}{0}
{combining good and evil}{1}
{knowing one another intimately}{0}
{learning to distinguish between good and evil}{0}
\qstop

\qpaper{74}{Adam and Eve}

\qstart{Could Adam \&\ Eve communicate with each other and their immediate children over a distance of 80 kilometres?}
{yes}{1}
{no}{0}
\qstop

\qstart{What was the serial number of Adam and Eve of Urantia?}
{10,311}{0}
{14,311}{1}
{18,311}{0}
{20,311}{0}
{6,666}{0}
{66,666}{0}
\qstop

\qstart{When did Adam and Eve appear?}
{on the sixth day of creation, about 6,000 years ago}{0}
{35,914 B.C.}{1}
{335,437,011 B.C.}{0}
{4,559 B.C.}{0}
{236,992 B.C.}{0}
\qstop

\qstart{How long did it take to rematerialize the bodies of Adam and Eve after they arrived from Jerusem on seraphic transport?}
{1 day}{0}
{7 days}{0}
{10 days}{1}
{12 days}{0}
{40 days}{0}
\qstop

\qstart{At rematerialization of Adam and Eve, who regained consciousness first?}
{Adam}{0}
{Eve}{0}
{both simultaneously}{1}
\qstop

\qstart{What was the height of Adam and Eve?}
{1.65\,m}{0}
{1.8\,m}{0}
{2.2\,m}{0}
{2.4\,m}{1}
{2.8\,m}{0}
{3.1\,m}{0}
{3.5\,m}{0}
\qstop

\qstart{What form of government did Adam and Eve find upon their arrival on Urantia?}
{democracy}{0}
{theocracy}{0}
{oligarchy}{0}
{no government worthy of a name}{1}
\qstop

\qstart{How many children did Adam \&\ Eve bear on this planet in total, aside from Cain and Sansa?}
{42}{0}
{64}{0}
{105}{1}
{501}{0}
{998}{0}
{12,000}{0}
\qstop

\qstart{Adam \&\ Eve fathered 105 children. After 4 generations, what did this number increase to in pure line descendants?}
{1,647}{1}
{12,547}{0}
{58,012}{0}
{187,022}{0}
\qstop

\qstart{What was the name of the firstborn son of Adam and Eve born on this planet?}
{Cain}{0}
{Abel}{0}
{Adamson}{1}
{Eveson}{0}
{Seth}{0}
\qstop

\qstart{What was the name of the second son of Adam and Eve born on this planet?}
{Cain}{0}
{Abel}{0}
{Adamson}{0}
{Eveson}{1}
{Seth}{0}
\qstop

\qstart{At what age did Adamic children cease to nurse the mother's breast?}
{eight months}{0}
{nine months}{0}
{one year}{1}
{one and a half years}{0}
{two years}{0}
{three years}{0}
\qstop

\qstart{How many times a day did the members of Adam's family eat?}
{once, shortly after noontime}{1}
{twice, morning and evening}{0}
{three times}{0}
{five times}{0}
{six times (like Hobbits)}{0}
\qstop

\qstart{How did Eve nourish her children after they ceased to take the mother's breast before they grew teeth?}
{by milk of animals}{0}
{by milk of nuts and fruit juice}{1}
{by cooked porridge}{0}
\qstop

\qstart{Adamic children attended school until they were ...}
{10}{0}
{12}{0}
{14}{0}
{16}{1}
{18}{0}
{22}{0}
{26}{0}
\qstop

\qstart{At what age did Adamic children become eligible for marriage?}
{14}{0}
{16}{0}
{18}{0}
{20}{1}
{25}{0}
{30}{0}
\qstop

\qstart{Who taught the younger children of Adam at school?}
{they taught themselves}{0}
{the elder children}{1}
{specially appointed instructors}{0}
{morontia visitors}{0}
{seraphic guardians}{0}
{Secondary Midwayers}{0}
{Primary Midwayers}{0}
\qstop

\qstart{When Adam and Eve left the Garden, their family consisted of ...}
{1 generation}{0}
{2 generations}{0}
{3 generations}{0}
{4 generations}{1}
{5 generations}{0}
{6 generations}{0}
\qstop

\qstart{When Adam and Eve left the Garden, their family consisted of ...}
{989 pure\hyp{}line descendants}{0}
{689 pure\hyp{}line descendants}{0}
{2,011 pure\hyp{}line descendants}{0}
{1,647 pure\hyp{}line descendants}{1}
{2,912 pure\hyp{}line descendants}{0}
\qstop

\qstart{How long did Adam and Eve live in the Garden before the default?}
{66 days}{0}
{6 months}{0}
{7 years}{0}
{37 years}{0}
{117 years}{1}
{122 years}{0}
{666 years}{0}
\qstop

\qstart{How many children did Adam and Eve have before coming to this planet?}
{12}{0}
{100}{1}
{none}{0}
{3}{0}
\qstop

\qpaper{75}{The Default of Adam and Eve}

\qstart{Do the divine plans require that Adam \&\ Eve themselves should mate with the planetary mortals?}
{yes}{0}
{no}{1}
\qstop

\qstart{Why is it not surprising that missteps occur in the affairs of the evolutionary universes, with imperfection, disagreement, friction, and misunderstanding? }
{It is evidence of the fact and the act of personality in the Universe}{1}
{It is evidence of the fact that the First Great Source and Center is not just a force but also a personality}{1}
{It is evidence that our universe is personal and progressive and not merely mechanical or passively perfect}{1}
{It is proof that if our existence is dominated by Personality then we can be assured of the possibility of personality survival, growth, experience and adventure}{1}
{Because perfection is our goal, not our origin}{1}
\qstop

\qstart{How did the inhabitants of the garden react on finding out what happened to Eve?}
{Were very understanding of Cano and Serapatatia's motives}{0}
{Declared war on a nearby Nodite settlement utterly destroying them, including Cano}{1}
{Banished her from the garden and chose a new leader and mate for Adam}{0}
{Punished her with forty stripes save one and then considered the matter closed}{0}
\qstop

\qstart{The more superior stocks of Urantia now contain inheritance factors derived from four separate sources. Name them.}
{Sangik}{1}
{Adamic}{1}
{Orange}{0}
{Green}{0}
{Nodite}{1}
{Indigo}{0}
{Andonite}{1}
\qstop

\qstart{Under normal conditions the first work of a Planetary Adam and Eve would be the co-ordination and blending of the races. But on Urantia such a project seemed just about hopeless. Why?}
{The races had never been purged of their retarded and defective strains}{1}
{Urantia was an experimental, and rebellion seared world}{1}
{Because of wide-spread cannibalism}{0}
\qstop

\qstart{In our ascent to Paradise, at which point would it be advisable to attempt short cuts or circumventions to the established and divine plan?}
{Never}{1}
{Whenever it is deemed appropriate}{0}
{Onwards in our ascension from Jerusem}{0}
{During the sojourn on the perfect spheres of Havona}{0}
{During the studies in the universities of the minor sector}{0}
\qstop

\qstart{What was the cause of the Adamic default?}
{Eve ate the apple from the tree of knowledge of good and evil}{0}
{Eve fell into Caligastia's trap by embarking on a plan to accelerate world improvement, thereby modifying the divine plans}{1}
\qstop

\qstart{Which of these was the father of Cain?}
{Adam}{0}
{Cano}{1}
{Andon}{0}
{Satan}{0}
{Abraham}{0}
{Lucifer}{0}
\qstop

\qstart{Until what age were Adamic children considered incapable of making independent decisions (``prechoice age'')?}
{12 years}{0}
{18 years}{0}
{20 years}{1}
{30 years}{0}
{40 years}{0}
\qstop

\qstart{How did the members of Adam's family cook their food?}
{roasted on open fire}{0}
{baked in stone ovens}{0}
{didn't cook at all --- ate it raw}{1}
{boiled in the water}{0}
\qstop

\qstart{Following the default, what did the Melchizedeks advise Adam to do?}
{They refused to advise him as they had been forbidden to interfere with the personal plans of Adam and Eve}{1}
{They advised Adam and Eve to return to Jerusem immediately}{0}
{They promised their friendly cooperation}{1}
\qstop

\qpaper{76}{The Second Garden}

\qstart{The transgression of Adam and Eve was ...}
{an error of judgment}{1}
{the sin of conscious and deliberate rebellion}{0}
\qstop

\qstart{Were Adam and Eve able to see midwayers, angels, Melchizedeks and Caligastia after the default?}
{yes, but only for 100 years}{1}
{yes, for as long as they lived}{0}
{no}{0}
\qstop

\qstart{Adam and Eve were indwelt by Thought Adjusters...}
{when they were citizens of Jerusem}{0}
{during their life in the first garden prior to the default}{0}
{after they were reduced to mortal status subsequent to the default}{1}
\qstop

\qstart{The name of the first child of Adam and Eve to be born in the second garden was ...}
{Cain}{0}
{Abel}{1}
{Seth}{0}
{Sansa}{0}
{Adamson}{0}
\qstop

\qstart{In which year did Cain slay Abel?}
{35,776 B.C.}{1}
{3,600 B.C.}{0}
{no record of the date}{0}
{27,561 B.C.}{0}
\qstop

\qstart{How old were Cain and Abel when the tension between them was finally resolved?}
{18 and 20}{0}
{20 and 18}{1}
{36 and 30}{0}
{36 and 34}{0}
{136 and 134}{0}
{16 and 14}{0}
\qstop

\qstart{How did Adam and Eve find out about the death of Abel?}
{telepathically}{0}
{dogs brought the flocks back without their master}{1}
{Cain told them}{0}
{Cain sent the message by a servant}{0}
{by a Secondary Midwayer}{0}
\qstop

\qstart{What was the name of Cain's wife?}
{Remona}{1}
{Ratta}{0}
{Melpomena}{0}
{Muzzah}{0}
\qstop

\qstart{What was the ``mark'' which Cain received?}
{Tatoo}{0}
{Thought Adjuster}{1}
{Ear-ring}{0}
{Burn on the forehead}{0}
\qstop

\qstart{Who were Andites?}
{a separate Sangik race}{0}
{offspring of Andonites}{0}
{same as Andonites}{0}
{result of the union of Adamites and Sangik races}{0}
{result of the union of Adamites and Nodites}{1}
\qstop

\qstart{How old was Adam when he died?}
{930}{0}
{730}{0}
{530}{1}
{130}{0}
{86}{0}
{40}{0}
\qstop

\qstart{What was the cause of Adam's death?}
{weakened heart}{0}
{kidneys failure}{0}
{poisoning}{0}
{earthquake}{0}
{killed by his own son}{0}
{old age}{1}
\qstop

\qstart{How old was Eve when she died?}
{930}{0}
{730}{0}
{511}{1}
{130}{0}
{86}{0}
{40}{0}
\qstop

\qstart{What was the cause of Eve's death?}
{poisoning}{0}
{old age}{0}
{weakened heart}{1}
{earthquake}{0}
{kidneys failure}{0}
{killed by his own son}{0}
\qstop

\qstart{Who was Laotta?}
{mother of Adam's child}{1}
{wife of Lot}{0}
{daughter of Abraham and Sarah}{0}
{mother of Cain}{0}
\qstop

\qstart{What did Adam do after committing default?}
{committed suicide}{0}
{wandered in solitude for 30 days}{1}
{killed Eve and married Laotta}{0}
{killed Laotta and begged Eve's forgiveness}{0}
\qstop


\qstart{What happened to Laotta, the mother of Sansa?}
{died while giving birth to Sansa}{1}
{died of old age}{0}
{was killed by the Nodites}{0}
{committed suicide}{0}
\qstop

\qpaper{77}{The Midway Creatures}

\qstart{What do the 60 rebel members of Caligastia's staff, and the 44 modified Andonites who followed them into rebellion, have in common?}
{They were the ancestors of the Nodites}{1}
{They were the 8\ts{th} race to appear on Urantia}{1}
{Their offspring gave rise to the legend of the biblical ``Nephilim''}{1}
{Their offspring gave rise to the legends of the ``mighty men of old''}{1}
\qstop

\qstart{50,000 years after the death of Nod, building of the Tower of Babel commenced and was named after Bablot, its architect and builder, and descendant of Nod. Where was it located?}
{Dilmun}{1}
{Syria}{0}
{Turkey}{0}
{Mount Ararat}{0}
\qstop

\qstart{12,000 years ago the Andites, the mixed races of the Nodites and Adamites, undertook to build a new temple on the ruins of the first Tower of Babel. What transpired?}
{The Hebrews walked around it 7 times whilst blowing their trumpets until it collapsed}{0}
{It fell under its own weight}{1}
{It remained incomplete for the second time}{0}
{Their languages were confused and they stopped building}{0}
\qstop

\qstart{The internal Nodite conflict over the tower of Babel greatly reduced the number of purer Nodites and was in many ways responsible for their failure to establish a great civilisation. What happened after 120,000 years of decline of Nodite culture?}
{It was upstepped by Adamic infusion}{1}
{The Melchizedek receivers intervened}{0}
{It completely vanished from the face of the earth}{0}
\qstop

\qstart{Immediately following the Bablot conflict, three out of the four great Nodite centers were established. Which of the following isn't one of them?}
{The western (Syrian) Nodites --- who contributed much to the later appearing Assyrian stock}{0}
{The eastern (west/south west Iran) Elamite Nodites (``the Land of Nod'')}{0}
{The central (pre-Sumerian) Nodites at the mouth of the Tigris and Euphrates rivers --- founders of the historic Sumerians}{0}
{The first settlement, before the Bablot conflict, the northern Nodites and Amadonites (the Vanites) --- descendants of Van and Amadon not involved with the leadership of Nod and his successors --- moved to settlements around Lake Van}{0}
{The southern (Jordanian) Nodites, founders of the Nabataeans}{1}
\qstop

\qstart{After the submergence of Dalamatia 200,000 years ago, where did the Nodites move to found a new city as their racial and cultural headquarters?}
{Dilmun}{1}
{Egypt}{0}
{Palestine}{0}
{North Polar region}{0}
{South Polar region}{0}
\qstop

\qstart{The Nodites were divided as to the plans for the Tower of Babel. There were three differing views as to the purpose of building the tower. Which view is \bibemph{not} one of them?}
{As a memorial of Nodite history and racial superiority}{0}
{To commemorate the Dilmun culture which was foreseen as becoming a great center of commerce, art and manufacture}{0}
{For the worship of the Father of all, and for making atonement for the folly of their progenitors in participating in the Caligastia rebellion. That the whole purpose of the new city should be to take the place of Dalamatia}{0}
{As a memorial to Daligastia, in whose honour the city of Dalamatia was named}{1}
\qstop

\qstart{The differing Nodite views as to the purpose of the Tower of Babel grew so contentious that all building work stopped after 4.5 years. One of the groups, the religious group, dispersed after it was voted down. What happened to the remaining two groups?}
{They fought until near obliteration}{1}
{They joined forces and completed the building of the tower}{0}
{They destroyed the tower}{0}
{They stopped understanding each other's language because God caused their confusion}{0}
\qstop

\qstart{Lake Van and Mount Ararat (the sacred mountain of northern Mesopotamia) is where many traditions originated. Which two of these stories were woven into the later Jewish scriptures?}
{Noah and the universal flood}{1}
{Moses receiving the Law on mount Sinai}{1}
{Eve eating the fruit of the forbidden tree}{0}
{Jonah and the whale}{0}
\qstop

\qstart{How many primary midwayers were produced by each pair of Caligastia's corporeal staff of 100, and what was the total of midwayers which came into being?}
{1,000/50,000}{1}
{100/5,000}{0}
{2,000/100,000}{0}
\qstop

\qstart{What is the origin of primary midwayers?}
{offspring of Caligastia 100}{1}
{offspring of Adamson \&\ Ratta}{0}
{offspring of Adam \&\ Eve}{0}
\qstop

\qstart{How many primary midwayers were there originally?}
{1,111}{0}
{1,286}{0}
{1,984}{0}
{50,000}{1}
{99,984}{0}
\qstop

\qstart{Who is the eldest Primary Midwayer?}
{1-2-3 the First}{1}
{the Father Midwayer}{0}
{Adamson}{0}
{Adam}{0}
\qstop

\qstart{What or who is A-B-C the First?}
{Primary Midwayer}{0}
{Secondary Midwayer}{1}
{Melchizedek}{0}
{Seraphim}{0}
{Cherubim}{0}
\qstop

\qstart{How many secondary midwayers were there originally?}
{1,111}{0}
{1,286}{0}
{1,984}{1}
{50,000}{0}
{99,984}{0}
\qstop

\qstart{What is the origin of the secondary midwayers?}
{Salvington}{0}
{Uversa}{0}
{offspring of the 16 invisible children of Adamson and Ratta}{1}
{offspring of Adam and Eve}{0}
{offspring of primary midwayers}{0}
\qstop

\qstart{Where can archaeological evidence be found of the later day descendants of the Nodites?}
{The clay tablets listing Sumerian kings}{1}
{In heiroglyphic records on Egyptian temples}{0}
{In the ancient ruins of Knossos, Crete}{0}
{Underneath the Western Wall in Jerusalem}{0}
{On the mount Ararat}{0}
\qstop

\qstart{How many Andonites contributed their germ plasm to the members of Planetary Prince's staff?}
{7}{0}
{12}{0}
{100}{1}
{5000}{0}
{144,000}{0}
{1 million}{0}
\qstop

\qpaper{78}{The Violet Race after the Days of Adam}

\qstart{The violet race consisted of...}
{pure Adamites only}{0}
{Adamites and Adamsonites}{1}
{Andites and Andonites}{0}
{mixture of blue and red races}{0}
\qstop

\qstart{How many Adamites were living on Urantia by 19,000 B.C.?}
{1 million}{0}
{4.5 million}{1}
{25 millions}{0}
{100 millions}{0}
\qstop

\qstart{When did Adamites cease to exist as a race upon Urantia?}
{15,000 B.C.}{1}
{6,000 B.C.}{0}
{600 B.C.}{0}
{300 A.D.}{0}
\qstop

\qpaper{79}{Andite Expansion in the Orient}

\qstart{When did the main body of the yellow race enter China?}
{600,000 years ago}{0}
{300,000 years ago}{1}
{200,000 years ago}{0}
{80,000 years ago}{0}
{3,000 years ago}{0}
{1,500 years ago}{0}
\qstop

\qpaper{80}{Andite Expansion in the Occident}

\qstart{Who was the leader of 375 most beautiful men since the days of the first Eden which settled in Greece about 10,000 B.C.?}
{Sato, a direct descendant of Adamson and Ratta}{1}
{Hercules}{0}
{Zeus}{0}
{Alexander the Great}{0}
\qstop

\qstart{What happened to the remnants of Neanderthal races?}
{exterminated by the Adamites}{1}
{became extinct}{0}
{exterminated by the Nodites}{0}
\qstop

\qstart{When was goat domesticated?}
{5000 B.C.}{1}
{2000 B.C.}{0}
{600 B.C.}{0}
{25,000 B.C.}{0}
\qstop

\qstart{When did the Andites disappear?}
{2000 B.C.}{1}
{3000 B.C.}{0}
{12,000 B.C.}{0}
{640 A.D.}{0}
\qstop

\qstart{Who were the ancestors of the so\hyp{}called Nordic races, the forefathers of the Scandinavian, German, and Anglo-Saxon peoples?}
{Nodites}{0}
{Andonites}{0}
{Andites}{1}
{green men}{0}
\qstop

\qpaper{81}{Development of Modern Civilization}

\qstart{Did Stone, Bronze and Iron Ages exist at the same time in different localities?}
{yes}{1}
{no}{0}
\qstop

\qpaper{82}{The Evolution of Marriage}

\qpaper{83}{The Marriage Institution}

\qpaper{84}{Marriage and Family Life}

\qstart{What is the effect of shifting parental responsibility to state or church on the welfare and advancement of civilization?}
{no effect}{0}
{beneficial}{0}
{suicidal}{1}
\qstop

\qstart{Modern problems of child culture are rendered increasingly difficult by:}
{The large degree of race mixture}{1}
{Artificial and superficial education}{1}
{Inability of the child to gain culture by imitating parents --- the parents are absent from the family picture so much of the time}{1}
\qstop

\qpaper{85}{The Origins of Worship}

\qpaper{86}{Early Evolution of Religion}

\qstart{What is the natural state of the savage mind?}
{anxiety}{1}
{anger}{0}
{joy}{0}
{stillness}{0}
\qstop

\qpaper{87}{The Ghost Cults}

\qpaper{88}{Fetishes, Charms, and Magic}

\qstart{What was mankind's first toy?}
{mammoth bone}{0}
{preserved umbilical cord}{1}
{fish bone}{0}
{preserved skull}{0}
{fish eyes}{0}
\qstop

\qstart{What was mankind's first necklace?}
{rope set with fish eyes}{0}
{mammoth sinew set with precious stones}{0}
{umbilical cord set with pearls}{1}
\qstop

\qstart{Moses' injunction against fetishes became ...}
{the Law of God}{0}
{the Word of God}{0}
{the supreme fetish}{1}
\qstop

\qpaper{89}{Sin, Sacrifice, and Atonement}

\qstart{Which animal was domesticated first?}
{horse}{0}
{dog}{1}
{cow}{0}
{pig}{0}
{lion}{0}
\qstop

\qpaper{90}{Shamanism --- Medicine Men and Priests}

\qpaper{91}{The Evolution of Prayer}

\qstart{Which of these two came first?}
{prayers}{1}
{belief in spirits}{0}
\qstop

\qpaper{92}{The Later Evolution of Religion}

\qstart{Which is the most recent of all evolutionary (manmade) religions?}
{Buddhism}{0}
{Christianity}{0}
{Islam}{0}
{Sikhism}{1}
{Zoroastrianism}{0}
{Shinto}{0}
{Jainism}{0}
{Judaism}{0}
{Hinduism}{0}
\qstop

\qstart{Which is the most ancient of all evolutionary (manmade) religions?}
{Buddhism}{0}
{Christianity}{0}
{Islam}{0}
{Sikhism}{0}
{Zoroastrianism}{0}
{Shinto}{0}
{Jainism}{0}
{Judaism}{0}
{Hinduism}{1}
\qstop

\qstart{The combined teachings of which religions were synthesized by Nanak and his followers into Sikhism?}
{Islam, Hinduism, and Buddhism}{1}
{Islam, Hinduism, and Christianity}{0}
{Islam, Zoroastrianism, and Mithraism}{0}
\qstop

\qpaper{93}{Machiventa Melchizedek}

\qstart{Whom did Melchizedek invite to his school in Salem?}
{Abraham}{0}
{Terah and his whole family}{0}
{Nahor}{0}
{Abraham and Nahor}{1}
\qstop

\qstart{Which of these was the teacher of Abraham?}
{Lutentia}{0}
{Lucifer}{0}
{Satan}{0}
{Tabamantia}{0}
{Machiventa Melchizedek}{1}
{Mantutia Melchizedek}{0}
{The Father Melchizedek}{0}
{Yahweh, the God of Israel}{0}
\qstop

\qstart{Who introduced the tithing system into the schools of Melchizedek?}
{Melchizedek}{0}
{Abraham}{1}
{Lot}{0}
{Sarah}{0}
\qstop

\qstart{The original records that served as a base for the Old Testament were based on the teachings of Melchizedek and were full and replete. Where were they edited en masse to almost completely obliterate all traces of Melchizedek teachings and turned into the confusing and self-contradictory body we have today?}
{In Babylon}{1}
{After return from Babylon}{0}
{Prior to Babylon Captivity}{0}
{In medieval times}{0}
{Jews continue to edit them today}{0}
\qstop

\qstart{Why so few of the Jews recognized and received the Son of God when he was born as Jesus of Nazareth?}
{Because their fathers in Babylon distorted and corrupted the teachings of Melchizedek (when writing what we know today as ``Old Testament'') and edited out all the references to his promise of the coming bestowal Son}{1}
{Because it is in their nature to be distrusting and suspicious}{0}
{Because the Priests and Pharisees didn't recognize him}{0}
\qstop

\qpaper{94}{The Melchizedek Teachings in the Orient}

\qstart{Which of these is \bibemph{not} a member of Trimurti, the supreme trinity of Hinduism?}
{Brahma}{0}
{Siva}{0}
{Vishnu}{0}
{Indra}{1}
\qstop

\qstart{The religion of Buddhism is based on the teachings of ...}
{Lao-tse}{0}
{Gautama Siddhartha}{1}
{Confucius (Kung Fu-tze)}{0}
{Ikhnaton}{0}
{Krishna}{0}
\qstop

\qstart{Which of these were the main commandments of Gautama Siddhartha?}
{You shall not kill}{1}
{You shall not steal}{1}
{You shall not be unchaste}{1}
{You shall not lie}{1}
{You shall not drink intoxicating liquors}{1}
\qstop

\qpaper{95}{The Melchizedek Teachings in the Levant}

\qstart{In 6,000 years only ... great prophets arose among the Egyptians.}
{2}{0}
{3}{0}
{4}{1}
{5}{0}
{10}{0}
{12}{0}
{28}{0}
\qstop

\qstart{The four great prophets that appeared in Egypt are...}
{Moses}{1}
{Amenemope}{1}
{Ikhnaton}{1}
{Okhban}{1}
{Onagar}{0}
{Joseph}{0}
{Abraham}{0}
{Jeremiah}{0}
\qstop

\qstart{Which evolutionary religion perpetuated the teaching of Dalamatia and Eden about the Seven Master Spirits?}
{Zoroastrianism}{1}
{Judaism}{0}
{Christianity}{0}
{Islam}{0}
{Buddhism}{0}
{Hinduism}{0}
{Jainism}{0}
{Sikhism}{0}
\qstop

\qstart{How many psalms (credited to Hebrew authorship) were written by the Egyptian prophet-king Ikhnaton?}
{all of them}{0}
{none}{0}
{1}{0}
{2}{0}
{4}{0}
{5}{0}
{12}{1}
{16}{0}
{28}{0}
\qstop

\qstart{Who is the author of chapters 15,17,20,22:17-24:22 of the ``Hebrew'' book of Proverbs?}
{Amenemope the Egyptian}{1}
{Ikhnaton the Egyptian}{0}
{Okhban the Egyptian}{0}
{Solomon}{0}
{David}{0}
{Moses}{0}
{Isaiah}{0}
\qstop

\qpaper{96}{Yahweh --- God of the Hebrews}

\qpaper{97}{Evolution of the God Concept among the Hebrews}

\qstart{How many of David's soldiers were Baalites?}
{None}{0}
{25\%}{0}
{50\%}{0}
{80\%}{1}
{100\%}{0}
\qstop

\qstart{What was Micah prophesying about when he said: ``But every man shall sit under his own vine, and no one shall make him afraid, for all people will live, each one according to his understanding of God.'' }
{the end of priestcraft and superstition}{1}
{the times of Jewish rule over the whole world}{0}
{the day of the Jewish Messiah coming to rule the nations}{0}
{the material plenty throughout the whole world}{0}
\qstop

\qstart{How did Solomon son of David bankrupt the nation?}
{by his lavish court and elaborate building program}{1}
{by waging wars}{0}
{by his idleness}{0}
\qstop

\qstart{What prevented the overthrow of the whole bloody ceremonial of the Hebrew ritual of worship by the fearless prophets Isaiah, Micah and Obadiah?}
{The stubborn resistance of the priests}{1}
{The ``Lord God of Israel'' who supposedly instituted these bloody rituals and sacrifices}{0}
{The common people}{0}
{The orders of the King of Israel who ruled then}{0}
{The ``Most Highs'' who supposedly ``rule in the kingdoms of men''}{0}
\qstop

\qpaper{98}{The Melchizedek Teachings in the Occident}

\qpaper{99}{The Social Problems of Religion}

\qpaper{100}{Religion in Human Experience}

\qstart{What state of mind virtually thwarts the work of the Thought Adjuster?}
{fear and anxiety}{1}
{too much joy}{0}
{deep contemplation}{0}
\qstop

\qstart{What is the result of elevating purely personal evaluations to the levels of absolutes?}
{sin}{0}
{evil}{1}
{good}{0}
{iniquity}{0}
\qstop

\qstart{Should the trancelike state of visionary consciousness be cultivated as a religious experience?}
{no}{1}
{yes}{0}
\qstop

\qpaper{101}{The Real Nature of Religion}

\qpaper{102}{The Foundations of Religious Faith}

\qpaper{103}{The Reality of Religious Experience}

\qpaper{104}{Growth of the Trinity Concept}

\qpaper{105}{Deity and Reality}

\qpaper{106}{Universe Levels of Reality}

\qpaper{107}{Origin and Nature of Thought Adjusters}

\qstart{What is the average age of receiving the Thought Adjuster on Urantia?}
{6 years}{1}
{7 years}{0}
{20 years}{0}
{40 years}{0}
\qstop

\qpaper{108}{Mission and Ministry of Thought Adjusters}

\qstart{Prior to the day of Pentecost, Thought Adjusters have been universally bestowed upon all normal minds of mortal status on Urantia. TRUE or FALSE?}
{TRUE}{0}
{FALSE}{1}
\qstop

\qpaper{109}{Relation of Adjusters to Universe Creatures}

\qstart{Upon attainment of which of the seven cosmic circles of intellectuality and spirituality the human is assigned a personal seraphic guardian?}
{first}{0}
{second}{0}
{third}{1}
{fourth}{0}
{fifth}{0}
{sixth}{0}
{seventh}{0}
\qstop

\qstart{Did Jesus have a Thought Adjuster?}
{yes}{1}
{no}{0}
\qstop

\qstart{Who did Jesus' Thought Adjuster previously indwell?}
{Machiventa Melchizedek}{1}
{Abraham}{0}
{No-one}{0}
{Enoch}{0}
{Elijah}{0}
{Isaiah}{0}
\qstop

\qpaper{110}{Relation of Adjusters to Individual Mortals}

\qstart{If a human is assigned a personal seraphic guardian does he stay with that human until death or can he leave him for some misdeed?}
{yes, stays until death}{1}
{no, he can leave the mortal if he chooses not to do the Father's will anymore}{0}
\qstop

\qstart{What happens to the human's material body upon fusion with the indwelling Thought Adjuster?}
{It glows}{0}
{It is consumed}{1}
{There are no visible signs}{0}
{It becomes invisible}{0}
\qstop

\qstart{What happens to a human upon making irrevocable decision to abide by the Father's will?}
{nothing}{0}
{a personal seraphic guardian is assigned}{0}
{fusion with Adjuster}{1}
{he is mustered into the Reserve Corps of Destiny}{0}
{his body begins to glow with a bluish light}{0}
\qstop


\qstart{Do the adjutant mind-spirits continue to function on the mansion worlds?}
{yes}{0}
{no}{1}
\qstop

\qpaper{111}{The Adjuster and the Soul}

\qpaper{112}{Personality Survival}

\qstart{On average, how many mortals of Urantia are resurrected after physical death?}
{0.01\%}{0}
{1\%}{0}
{56\%}{0}
{95\%}{0}
{99\%}{0}
{100\%}{0}
{unrevealed}{1}
\qstop

\qstart{Can the personality identity survive independently from the survival of the morontia soul?}
{yes}{0}
{no}{1}
\qstop

\qstart{Are those resurrected on the mansion worlds permitted to send messages to their loved ones here?}
{yes}{0}
{no}{1}
\qstop

\qstart{Does the guardian seraphim abandon a living person in the event of spiritual death (departure of Thought Adjuster)?}
{yes}{0}
{no}{1}
\qstop

\qpaper{113}{Seraphic Guardians of Destiny}

\qstart{When one of the seraphic pair is recharging with the life energy, who does the duty of recording?}
{nobody}{0}
{the other seraphim of the pair}{0}
{the assisting cherubim}{1}
\qstop

\qstart{Do individual seraphim have names or only numbers?}
{no, only numbers}{0}
{yes, they have personal names}{1}
\qstop

\qstart{Prior to the last bestowal of Michael (Jesus of Nazareth) what was the criteria for assignment of seraphic guardians to mortals?}
{race}{1}
{intellect}{0}
{spirituality}{0}
{attainment of cosmic circles}{0}
{to the Jew first, and then to the Gentiles}{0}
\qstop

\qstart{Subsequent to the last bestowal of Michael (as Jesus of Nazareth) what was the criteria for assignment of seraphic guardians to mortals?}
{race}{0}
{intellect}{0}
{spirituality}{0}
{attainment of cosmic circles}{1}
{to the Jew first, and then to the Gentiles}{0}
\qstop

\qstart{What is the first assignment of a resurrected mortal?}
{Learning Satanian language}{0}
{Assisting seraphim}{1}
{Learning the tongue of Uversa}{0}
{Observing the stars}{0}
{Sending a message back to the relatives on Earth}{0}
\qstop

\qstart{Are all seraphic guardians called destiny guardians?}
{yes}{0}
{no}{1}
\qstop

\qpaper{114}{Seraphic Planetary Government}

\qpaper{115}{The Supreme Being}

\qpaper{116}{The Almighty Supreme}

\qpaper{117}{God the Supreme}

\qstart{Love is...}
{living and flexible}{0}
{best known by its spiritual flavour}{0}
{coherent, beauty attractive, goodness stabilizing}{0}
{alive, free, thrilling, and always moving}{1}
\qstop

\qpaper{118}{Supreme and Ultimate --- Time and Space}

\qpaper{119}{The Bestowals of Christ Michael}

\qstart{Who was left in charge of the celestial forces during Michael's third bestowal?}
{Gabriel of Salvington}{1}
{The Father Melchizedek}{0}
{Immanuel}{0}
{no one}{0}
\qstop
\qstart{Did the methods of universe administration improve after each of Michael's bestowal?}
{yes}{1}
{no}{0}
\qstop

\qstart{When was the first bestowal of Michael of Nebadon?}
{20 million years ago}{0}
{120 million years ago}{0}
{800 million years ago}{0}
{1 billion years ago}{1}
{4 billion years ago}{0}
{10 billion years ago}{0}
\qstop

\qstart{What was the time interval between two bestowals of Michael of Nebadon?}
{500 million years}{0}
{150 million years}{1}
{10 million years}{0}
{100,000 years}{0}
{500,000 years}{0}
\qstop

\qstart{At what time of day did Michael appear on the planet of his bestowal as a Melchizedek?}
{early morning}{0}
{noon}{1}
{late evening}{0}
{midnight}{0}
{unknown}{0}
\qstop

\qstart{How many Melchizedeks witnessed the disappearance of Michael at the end of his bestowal as a Melchizedek?}
{0}{0}
{1}{0}
{3}{1}
{4}{0}
{7}{0}
{thousands}{0}
\qstop

\qstart{At what time of day did Michael disappear from the planet of his bestowal as a Melchizedek?}
{early morning}{0}
{noon}{1}
{late evening}{0}
{midnight}{0}
{unknown}{0}
\qstop

\qstart{What was the name of system 11 in constellation 37?}
{Polonia}{0}
{Palonia}{1}
{Abbadonia}{0}
{Avalonia}{0}
{Panoptia}{0}
\qstop

\qstart{Which position did Michael of Nebadon fill during his second bestowal?}
{Acting System Sovereign}{1}
{Acting Executioner of the Ancients of Days}{0}
{Acting Supreme Judge of the System}{0}
{Observer}{0}
{Recorder}{0}
{Teacher}{0}
\qstop

\qstart{What was the name of the rebel System Sovereign of Palonia?}
{Lucifer}{0}
{Lutentia}{1}
{Balantia}{0}
{Tabamantia}{0}
{Serapatatia}{0}
{Gavalia}{0}
\qstop

\qstart{Did Lutentia accept Michael's offer of mercy?}
{yes}{0}
{no}{1}
\qstop

\qstart{At what time of day did Michael appear on the planet of his bestowal as a Lanonandek?}
{early morning}{0}
{noon}{1}
{late evening}{0}
{midnight}{0}
{unknown}{0}
\qstop

\qstart{Who requested a Material Son for the inhabited planet 217 of system 87 in constellation 61 700 million years ago?}
{Life Carriers}{1}
{Melchizedeks}{0}
{Planetary Prince}{0}
{Chief of Seraphim}{0}
{Mortal inhabitants of that planet}{0}
\qstop

\qstart{Was there a Material Daughter assigned to assist Michael during his bestowal as a Material Son?}
{yes}{0}
{no}{1}
\qstop

\qstart{At what time of day did Michael disappear from the planet of his bestowal as a Material Son?}
{early morning}{0}
{noon}{1}
{late evening}{0}
{midnight}{0}
{unknown}{0}
\qstop

\qpaper{120}{The Bestowal of Michael on Urantia}

\qpaper{121}{The Times of Michael’s Bestowal}

\qstart{The notion that Israel is still ``God's chosen people'' is...}
{divinely inspired and revealed truth}{0}
{delusion}{1}
\qstop

\qstart{Who wrote ``The Gospel according to Matthew''?}
{Matthew}{0}
{Isador}{1}
{Luke}{0}
{Mark}{0}
{Paul}{0}
{A slave named Cedes}{0}
\qstop

\qstart{Who wrote ``The Gospel according to Luke''?}
{Matthew}{0}
{Isador}{0}
{Luke}{1}
{Mark}{0}
{Paul}{0}
{A slave named Cedes}{0}
\qstop

\qstart{When did Luke write his Gospel?}
{76\,A.D.}{0}
{70\,A.D.}{0}
{82\,A.D.}{1}
{86\,A.D.}{0}
{90\,A.D.}{0}
{99\,A.D.}{0}
\qstop

\qstart{When did Luke finish ``The Acts of the Apostles''?}
{76\,A.D.}{0}
{70\,A.D.}{0}
{80\,A.D.}{0}
{86\,A.D.}{0}
{90\,A.D.}{0}
{Never finished}{1}
\qstop

\qstart{What were Paul's disciples first called at Antioch?}
{Paulinians}{0}
{Christians}{1}
{Chasidim}{0}
{Good Antiochians}{0}
{Essenes}{0}
\qstop

\qpaper{122}{Birth and Infancy of Jesus}

\qstart{Who chose the race of Hebrews for Michael's bestowal?}
{Abraham}{0}
{Melchizedek}{0}
{Michael himself}{0}
{Gabriel of Salvington}{1}
{Gabriel of Avalon}{0}
{Chief of Seraphim}{0}
\qstop

\qstart{Who chose the family of Joseph for Michael's bestowal?}
{Abraham}{0}
{Gabriel of Avalon}{0}
{Gabriel of Salvington}{1}
{Melchizedek}{0}
{Chief of Seraphim}{0}
{Michael himself}{0}
\qstop

\qstart{Why was the family of Joseph chosen by Gabriel rather than Michael?}
{They flipped the coin and it fell on Gabriel}{0}
{Immanuel asked Gabriel to do this}{0}
{Michael asked Gabriel to do this}{0}
{So that Jesus might be born like all babies, having nothing to do with selecting his parents}{1}
{Because Michael was too busy preparing for the incarnation}{0}
\qstop

\qstart{Was Joseph a descendant of David \&\ Solomon?}
{yes }{0}
{no}{1}
\qstop

\qstart{Did Joseph descend from Andon \&\ Fonta, Nodites, Sumerians through Abraham?}
{yes}{1}
{no}{0}
\qstop

\qstart{When was John the Baptist born?}
{25 March 7 B.C.}{1}
{13 September 6 B.C.}{0}
{1 January 4 B.C.}{0}
{1 April 1 A.D.}{0}
\qstop

\qstart{Where was John the Baptist born?}
{Jericho}{0}
{Bethlehem}{0}
{City of Judah}{1}
{Alexandria}{0}
{Zaphon}{0}
{Philadelphia}{0}
{Gilead}{0}
\qstop

\qstart{What was the ``Star of Bethlehem''?}
{a brilliant evening star}{0}
{a sign from God}{0}
{Venus}{0}
{Mars}{0}
{a conjunction of Jupiter and Saturn}{1}
\qstop

\qstart{When was Jesus of Nazareth born?}
{21 August 7.~B.C.}{1}
{25 December 6.~B.C.}{0}
{25 December 4.~B.C.}{0}
{1 January 1.~A.D.}{0}
{18 September 6.~B.C.}{0}
{unknown}{0}
\qstop

\qpaper{123}{The Early Childhood of Jesus}

\qstart{How old was Jesus when he received his Thought Adjuster?}
{6 months}{0}
{3 years}{0}
{4 years}{1}
{5 years}{0}
{10 years}{0}
{18 years}{0}
\qstop

\qstart{When did Jesus receive his Thought Adjuster?}
{1\ts{st} January, 1\,B.C.}{0}
{10\ts{th} February, 1\,B.C.}{0}
{11\ts{th} February, 2\,B.C.}{1}
{21\ts{st} August, 1\,B.C.}{0}
{21\ts{st} August, 3\,B.C.}{0}
\qstop

\qstart{Which languages did Jesus speak?}
{Hebrew}{0}
{Hebrew \&\ Aramaic}{0}
{Hebrew, Aramaic \&\ Greek}{1}
\qstop

\qpaper{124}{The Later Childhood of Jesus}

\qstart{What age was Jesus when a messenger from Salvington said to him ``The hour has come. It is time that you began to be about your Father’s business''?}
{10}{0}
{12}{0}
{13}{1}
{14}{0}
{20}{0}
{21}{0}
{30}{0}
\qstop

\qpaper{125}{Jesus at Jerusalem}

\qstart{What was Jesus' attitude towards the doctrine of the wrath of God?}
{accepted it wholeheartedly}{0}
{accepted reluctantly}{0}
{refused to accept}{1}
\qstop

\qpaper{126}{The Two Crucial Years}

\qstart{How many siblings did Jesus have (including Amos, who died at an early age)?}
{0}{0}
{1}{0}
{2}{0}
{3}{0}
{4}{0}
{5}{0}
{6}{0}
{7}{0}
{8}{1}
\qstop

\qstart{Which book influenced Jesus to adopt as his inaugural title ``the Son of Man''?}
{Book of Enoch}{1}
{Daniel}{0}
{Ezekiel}{0}
\qstop

\qstart{How old was Jesus when he assumed family responsibility following the death of his father?}
{13}{0}
{14}{1}
{17}{0}
{18}{0}
{20}{0}
{30}{0}
\qstop

\qpaper{127}{The Adolescent Years}

\qstart{Who was the officer of the Galilean division of the party of Zealots?}
{Jesus}{0}
{Jesus' uncle, Simon}{1}
{Jesus' sister, Ruth}{0}
{Jesus' father, Joseph}{0}
\qstop

\qstart{What was the reason for estrangement between Jesus and his uncle Simon?}
{Jesus' refusal to accept the title of Messiah}{0}
{Simon's refusal to accept Jesus' leadership of the Zealots}{0}
{Jesus' refusal to join the party of Zealots}{1}
{Jesus' refusal to honour his uncle Simon in public}{0}
{Simon's refusal to learn Hebrew}{0}
\qstop

\qpaper{128}{Jesus’ Early Manhood}

\qpaper{129}{The Later Adult Life of Jesus}

\qstart{How old was Jesus when he left his family home?}
{16}{0}
{21}{0}
{27}{1}
{30}{0}
\qstop

\qstart{In what capacity did Jesus travel the Mediterranean with Gonod and Ganid?}
{Guide}{0}
{Interpreter and tutor}{1}
{Spiritual Mentor}{0}
\qstop

\qstart{By whom was Jesus first called ``the Master''?}
{Simon, called Peter}{0}
{John of Zebedee}{0}
{the Alpheus twins}{0}
{the employees of Zebedee}{1}
{the fishermen of Capernaum}{0}
\qstop

\qpaper{130}{On the Way to Rome}

\qstart{Which of these places did Jesus \bibemph{not} visit?}
{India}{1}
{Greece}{0}
{Malta}{0}
{America}{1}
{Rome}{0}
\qstop

\qstart{Why did Jesus not stop to say comforting words to a beggar in Naples?}
{Because his parents were sinners}{0}
{Because he was a great sinner}{0}
{Because he was evil}{0}
{Because he wasn't interested}{0}
{Because he was not of normal mind}{1}
\qstop

\qpaper{131}{The World’s Religions}

\qpaper{132}{The Sojourn at Rome}

\qstart{In which city did Jesus seek out and teach the religious leaders of the Mystery Cults, Stoics, \&\ Cynics?}
{Babylon}{0}
{Alexandria}{0}
{Rome}{1}
{Jerusalem}{0}
\qstop

\qstart{Who said that ``the spiritually blind individual who logically follows scientific dictation, social usage, and religious dogma... is destined to become an intellectual parrot, a social automaton, and a slave to religious authority''?}
{Confucius}{0}
{Jesus of Nazareth}{1}
{Simon Peter}{0}
{Judas Iscariot}{0}
{Matthew Levi}{0}
{John Zebedee}{0}
\qstop

\qstart{To whom did Jesus say ``...the revelations of God flash upon earth in the lives of the men who reveal God to their fellows''}
{Ganid}{1}
{Gonod}{0}
{Simon Peter}{0}
{Judas Iscariot}{0}
{Matthew Levi}{0}
\qstop

\qstart{Who taught that the ability to entertain error or experience evil will not be fully lost until the ascending human soul achieves final spirit levels?}
{Jesus of Nazareth}{1}
{stoics}{0}
{Pharisees}{0}
{Sadducees}{0}
\qstop

\qpaper{133}{The Return from Rome}

\qstart{Is self-consciousness the soul?}
{yes}{0}
{no}{1}
\qstop

\qstart{In which of Jesus' talks did he say ``Matter and spirit and the state intervening between them are three interrelated and interassociated levels of the true unity of the real universe''?}
{The Science Discourse}{1}
{Discourse on Reality}{0}
{Discourse on Time and Space}{0}
\qstop

\qstart{Who taught that ``The human mind early begins to manifest qualities which are supermaterial and the truly reflective intellect is not altogether bound by the limits of time''?}
{The Mystic Cults}{0}
{Pythagorus}{0}
{Jesus}{1}
{Peter}{0}
{Moses}{0}
\qstop

\qstart{To what was Jesus referring when he said ``they destroy unity and may terminate in mind disruption. Only a happy and unified mind is dedicated to the doing of the will of the Father''?}
{Unresolved conflicts}{1}
{Evil friends}{0}
{Materialism}{0}
{Differing opinions on religious matters}{0}
\qstop

\qstart{To whom was Jesus referring when he said ``They cannot possess a time self-consciousness, only a sensation-recognition and memory, and cannot conclude intelligent and reflective interpretations''?}
{children}{0}
{idiots}{0}
{animals}{1}
{sinners}{0}
{Jews}{0}
\qstop

\qpaper{134}{The Transition Years}

\qstart{How long did Jesus spend travelling during his ``transition years''?}
{1 year}{0}
{2 years}{0}
{3 years}{1}
{5 years}{0}
{12 years}{0}
\qstop

\qstart{Did Jesus ever give formal lectures?}
{yes (12 lectures in the city of Alexandria)}{0}
{yes (24 lectures in the city of Urmia)}{1}
{no}{0}
\qstop

\qpaper{135}{John the Baptist}

\qstart{Who was the leader of the Engedi colony of Nazarites?}
{John the Baptist}{0}
{John Zebedee}{0}
{Jesus of Nazareth}{0}
{Abner}{1}
\qstop

\qstart{How long did the ministry of John the Baptist last?}
{12 months}{0}
{15 months}{1}
{24 months}{0}
{36 months}{0}
{3 months}{0}
{40 months}{0}
\qstop

\qstart{How many penitents did John the Baptist baptize?}
{100}{0}
{1,000}{0}
{12,000}{0}
{36,500}{0}
{100,000}{1}
{200,000}{0}
{300,000}{0}
\qstop

\qpaper{136}{Baptism and the Forty Days}

\qstart{Why did Jesus destroy all his writings and anything material associated with his life?}
{To avoid superstitious relic worshipping}{1}
{He didn't produce any writings}{0}
{He did leave writings which were destroyed by the priests}{0}
\qstop

\qstart{How old was Jesus when he was baptised by John the Baptist?}
{31 years}{0}
{31½ years}{1}
{32 years}{0}
{32½ years}{0}
{8 days}{0}
{1 year}{0}
\qstop

\qstart{What did Jesus see above his head at his baptism?}
{a white dove}{0}
{his Thought Adjuster}{1}
{an angel}{0}
{optical illusion}{0}
{nothing}{0}
\qstop

\qstart{Did Jesus fuse with his Thought Adjuster?}
{no}{1}
{yes}{0}
\qstop

\qstart{Why did Jesus' Adjuster appear above his head at his baptism?}
{He took leave of Jesus, as the perfected human soul becoming a son of God, returning as an exalted Personalised Adjuster existing apart from Jesus but in constant communion with him}{1}
{To say to John the Baptist ``this is my beloved son in whom I am well pleased''}{0}
{To indwell someone else}{0}
{To comply with the Universal Rite of Baptism rule \#6}{0}
\qstop

\qstart{Where did Jesus go immediately after his baptism?}
{To the Perean hills for 40 days of isolation in order to formulate plans of proclaiming the Kingdom of God}{1}
{Returned to work}{0}
{Returned to his family }{0}
{Started recruiting apostles}{0}
\qstop

\qstart{Who did Jesus encounter in the Perean hills post baptism?}
{Gabriel \&\ the Constellation Father of Edentia}{1}
{Lucifer}{0}
{No-one --- he remained alone}{0}
{Satan}{0}
{Caligastia}{0}
\qstop

\qstart{What did Jesus achieve during his 6 week sojourn on Mount Hermon prior to baptism?}
{Achieved the circles of mind-understanding and personality-control}{0}
{Wrestled in spirit with Satan (representing Lucifer), and Caligastia in ``the great temptation''}{0}
{Both of these}{1}
{None of these}{0}
\qstop

\qstart{In which year did Jesus declare that ``his time had come'' and present himself for baptism?}
{26 A.D.}{1}
{29 A.D.}{0}
{30 A.D.}{0}
{20 A.D.}{0}
\qstop

\qstart{How many passages from the Scriptures did the rabbis collect by the time of Jesus, erroneously thinking they were prophetic of the Messiah?}
{Almost 500}{1}
{Almost 300}{0}
{Almost 100}{0}
{72}{0}
{12}{0}
\qstop

\qstart{What were James and John of Zebedee doing during the 40 days after Jesus' baptism?}
{Working}{0}
{Searching for Jesus}{1}
{Waiting for Jesus together with John the Baptist}{0}
\qstop

\qstart{Who was baptized by John together with Jesus?}
{James and John of Zebedee}{0}
{James and Jude, Jesus' brothers}{1}
{No one, he was alone}{0}
{Judas Iscariot}{0}
\qstop

\qpaper{137}{Tarrying Time in Galilee}

\qpaper{138}{Training the Kingdom’s Messengers}

\qstart{How many of Jesus' apostles were fishermen?}
{none}{0}
{3}{0}
{6--7}{1}
{10}{0}
{all 12}{0}
\qstop

\qpaper{139}{The Twelve Apostles}

\qstart{How many of his Apostles did Jesus personally select?}
{6}{1}
{all 12}{0}
{only Judas Iscariot}{0}
{7}{0}
{only Peter and Andrew}{0}
\qstop

\qstart{Which of the Twelve Apostles of Jesus were Judeans?}
{Peter and Andrew}{0}
{Matthew, John, James and Peter}{0}
{Matthew and Bartholomew}{0}
{Only Judas Iscariot}{1}
{All of them}{0}
\qstop

\qstart{Which of these Apostles did Jesus \bibemph{not} personally select?}
{Andrew}{0}
{Peter}{0}
{James}{0}
{John}{0}
{Philip}{0}
{Nathaniel}{0}
{Thomas}{1}
\qstop

\qstart{Which of these Apostles were \bibemph{not} put to death?}
{Andrew}{0}
{Peter}{0}
{James}{0}
{Philip}{0}
{Matthew}{0}
{Thomas}{0}
{Alpheus twins}{1}
\qstop

\qpaper{140}{The Ordination of the Twelve}

\qstart{Who was the first of the 12 Apostles ordained for public ministry?}
{Andrew}{0}
{Peter}{0}
{Judas Iscariot}{1}
{John Zebedee}{0}
{Nathantiel}{0}
{Thomas}{0}
\qstop

\qpaper{141}{Beginning the Public Work}

\qstart{After which event did Jesus say that ``evil spirits shall no more molest men''?}
{At Pentecost after the pouring out of his Spirit of Truth}{1}
{After the temptation on Mount Hermon}{0}
{He didn't say it}{0}
{At his baptism}{0}
\qstop

\qpaper{142}{The Passover at Jerusalem}

\qstart{In 1 Chronicles 21:1 it is said that Satan provoked David to number Israel, whereas in 2 Samuel 24:1 it is said that Lord (Yahweh) did this. How can this be?}
{Satan and the Lord Yahweh are the same being}{0}
{1 Chronicles was written after 2 Samuel and the later author did not dare to attribute evil to Yahweh, so he edited it to say ``Satan'' instead}{1}
{We cannot understand this apparent ``contradiction'', but we must dogmatically assert (contrary to fact or truth) that Bible is ``the perfect and infallible Word of God''. As long as we abide by this dogma, we should be ``okay''.}{0}
\qstop

\qpaper{143}{Going Through Samaria}

\qpaper{144}{At Gilboa and in the Decapolis}

\qstart{Why did Peter, James and John who so often accompanied Jesus on his long night vigils, never heard Jesus pray?}
{Jesus never prayed}{0}
{Jesus never prayed aloud, only in the spirit and in his heart, silently}{1}
{Jesus prayed in a ``strange tongue'' that they did not understand}{0}
{Jesus always told them to leave when he was about to pray}{0}
{they didn't listen carefully}{0}
\qstop

\qpaper{145}{Four Eventful Days at Capernaum}

\qstart{Can demoniacal possession occur since the day of Pentecost?}
{yes}{0}
{no}{1}
\qstop

\qpaper{146}{First Preaching Tour of Galilee}

\qpaper{147}{The Interlude Visit to Jerusalem}

\qpaper{148}{Training Evangelists at Bethsaida}

\qpaper{149}{The Second Preaching Tour}

\qpaper{150}{The Third Preaching Tour}

\qpaper{151}{Tarrying and Teaching by the Seaside}

\qpaper{152}{Events Leading up to the Capernaum Crisis}

\qpaper{153}{The Crisis at Capernaum}

\qpaper{154}{Last Days at Capernaum}

\qpaper{155}{Fleeing Through Northern Galilee}

\qpaper{156}{The Sojourn at Tyre and Sidon}

\qpaper{157}{At Caesarea\hyp{}Philippi}

\qpaper{158}{The Mount of Transfiguration}

\qstart{Who or what did Peter, James \&\ John see on the Mount of Transfiguration?}
{Jesus talking to Lucifer and Caligastia}{0}
{Jesus talking to Gabriel and the Father Melchizedek}{1}
{Jesus meditating}{0}
{Jesus talking to Moses and Elijah}{0}
{Jesus talking to Enoch and Elijah}{0}
{Jesus talking to aliens}{0}
\qstop

\qpaper{159}{The Decapolis Tour}

\qpaper{160}{Rodan of Alexandria}

\qpaper{161}{Further Discussions with Rodan}

\qpaper{162}{At the Feast of Tabernacles}

\qpaper{163}{Ordination of the Seventy at Magadan}

\qstart{Who were the women's evangelistic corps?}
{10 (later 12) women selected and commissioned by Jesus to teach the gospel of the kingdom and to minister to the sick}{1}
{24 speciallly selected members of the apostles' families}{0}
{12 wives of the 12 apostles}{0}
\qstop

\qstart{From whom did Jesus require to give up their wordly goods?}
{The 12 Apostles and the 70 specially trained gospel preachers}{1}
{All his disciples}{0}
{He left the decision to the individual}{0}
\qstop

\qpaper{164}{At the Feast of Dedication}

\qstart{Which of these were the friends and secret supporters of Jesus?}
{Nicodemus}{1}
{Joseph of Arimathea}{1}
{Annas}{0}
{Caiaphas}{0}
{Judas Iscariot}{0}
\qstop

\qpaper{165}{The Perean Mission Begins}

\qpaper{166}{Last Visit to Northern Perea}

\qstart{Who was the head of the church in Philadelphia?}
{James (Jesus' brother)}{0}
{Matthew}{0}
{Mark}{0}
{Abner}{1}
\qstop

\qpaper{167}{The Visit to Philadelphia}

\qpaper{168}{The Resurrection of Lazarus}

\qpaper{169}{Last Teaching at Pella}

\qpaper{170}{The Kingdom of Heaven}

\qpaper{171}{On the Way to Jerusalem}

\qpaper{172}{Going into Jerusalem}

\qpaper{173}{Monday in Jerusalem}

\qpaper{174}{Tuesday Morning in the Temple}

\qpaper{175}{The Last Temple Discourse}

\qpaper{176}{Tuesday Evening on Mount Olivet}

\qstart{When was the covenant between Israel and God abrogated and the plan to make the children of Abraham the light-bearers for the whole world shattered?}
{Midnight, Tuesday 4 April 30 A.D.}{1}
{15:30, Thursday 6 April 30 A.D.}{0}
{Noon, Tuesday 4 April 30 A.D.}{0}
{18:00, Wednesday 5 April 30 A.D.}{0}
\qstop

\qstart{What percentage of the Sanhedrin voted to put to death both the Son of God and Lazarus?}
{100\%}{1}
{95\%}{0}
{60\%}{0}
{80\%}{0}
{25\%}{0}
\qstop

\qstart{What did Jesus promise to send to mankind after his ascension to the Father?}
{Spirit of Truth}{0}
{Return to the world himself}{0}
{Both}{1}
\qstop

\qpaper{177}{Wednesday, the Rest Day}

\qpaper{178}{Last Day at the Camp}

\qpaper{179}{The Last Supper}

\qstart{Was the Last Supper the only ceremony which Jesus established?}
{yes}{1}
{no}{0}
\qstop

\qstart{Did the Last Supper replace the Passover remembrance of the emergence of the Hebrews from racial slavery with the emergence of the enslaved individual from the bondage of ceremonialism?}
{yes}{1}
{no}{0}
\qstop

\qstart{At the Last Supper, which seat did Judas Iscariot take?}
{the seat of honour on the left of Jesus}{1}
{the seat of honour on the right of Jesus}{0}
{the seat furthest from Jesus}{0}
{a spare seat without any preference}{0}
\qstop

\qstart{At the Last Supper, which seat did John Zebedee take?}
{the seat of honour on the left of Jesus}{0}
{the seat of honour on the right of Jesus}{1}
{the seat furthest from Jesus}{0}
{a spare seat without any preference}{0}
\qstop

\qpaper{180}{The Farewell Discourse}

\qpaper{181}{Final Admonitions and Warnings}

\qstart{Which disciple did Jesus instruct to remain close at hand from his arrest until the very end of the crucifixion?}
{Peter}{0}
{John Zebedee}{1}
{James}{0}
{Matthew}{0}
{Thomas}{0}
\qstop

\qpaper{182}{In Gethsemane}

\qstart{Prior to Jesus' arrest and in response to Jesus' prayers in the garden of Gethsemane a ... came down by his side and, speaking to him, touched him and strengthened him.}
{secondary midwayer}{0}
{primary midwayer}{0}
{mighty angel}{1}
{Melchizedek}{0}
\qstop

\qstart{Which 3 apostles did Jesus ask to stay with him whilst he prayed in the garden of Gethsemane?}
{Peter, James \&\ John}{1}
{Peter, John \&\ Andrew}{0}
{Matthew Levi, Thomas \&\ Nathaniel}{0}
{James, John \&\ Judas Iscariot}{0}
{Judas Iscariot \&\ Alpheus twins}{0}
\qstop

\qstart{In his prayer in the garden of Gethsemane, Jesus said ``If this cup may not pass, then would I drink it. Not my will, but yours, be done''. Why did God desire Jesus to ``drink this cup''?}
{To have the mortal experience from birth to natural death and the resurrection of the morontia}{1}
{To be an example to mankind on how to live and die}{0}
{To fulfill that which is written in the Hebrew Scriptures}{0}
\qstop

\qstart{To whom did Jesus say: ``The spirit is indeed willing, but the flesh is weak''?}
{Peter}{0}
{James}{0}
{John}{0}
{All three}{1}
\qstop

\qstart{What made Jesus say that the spirit is willing, but the flesh is weak?}
{Finding Peter,James \&\ John asleep at his most trying time in the Garden of Gethsemane}{1}
{Peter's habit of speaking without thinking}{0}
{Seeing his apostles vying for the seats closest to him at the Last Supper}{0}
\qstop

\qpaper{183}{The Betrayal and Arrest of Jesus}

\qstart{Why was John Zebedee permitted to remain near Jesus all the way through his trying experiences?}
{Roman law allowed prisoners to have a friend stand with him before the judgement bar}{1}
{A working of God}{0}
{Because he was a friend of high priest}{0}
{Because he was a relative of Annas}{0}
\qstop

\qstart{Was the torture and murder of Jesus by the Jews part of the Father's will?}
{yes}{0}
{no}{1}
\qstop

\qstart{Who was behind the plan of Jesus' torture and murder?}
{Lucifer}{0}
{The Romans}{0}
{Jewish priests}{1}
{Satan}{0}
{Caligastia}{0}
{Judas Iscariot}{0}
\qstop

\qstart{To whom did Jesus say ``They who take the sword shall perish by the sword''?}
{a Roman soldier}{0}
{Peter}{1}
{a zealot}{0}
\qstop

\qpaper{184}{Before the Sanhedrin Court}

\qstart{Why Judas Iscariot could not be used by the Sanhedrists as a witness in the ``trial'' of the Master?}
{Judas already killed himself}{0}
{Judas could not be found at the time of trial}{0}
{Jewish law specifically forbade the testimony of a traitor}{1}
\qstop

\qstart{How could the cock crow when Peter denied Jesus if it was against the law to keep poultry in the city of Jerusalem?}
{Peter's entire experience occurred in the courtyard of the palace of Annas on Mount Olivet. He did not follow Jesus to the palace of the high priest, Caiaphas.}{1}
{It wasn't a cock crowing.}{0}
\qstop

\qstart{Why did Annas make up his mind to murder Jesus even before his so-called ``trial'' by the Sanhedrin?}
{Jesus challenged the Jewish priests' authority}{0}
{His revenues were threatened by Jesus driving the money changers and commercial traders out of the temple}{1}
{He regarded Jesus as a blasphemer for claiming to be the Son of God}{0}
{He envied Jesus being treated as a prophet by the common people}{0}
\qstop

\qpaper{185}{The Trial Before Pilate}

\qstart{When was Jesus of Nazareth murdered by the Jews?}
{1 April 30 A.D.}{0}
{7 April 30 A.D.}{1}
{15 April 33 A.D.}{0}
{14 April 30 A.D.}{0}
\qstop

\qpaper{186}{Just Before the Crucifixion}

\qpaper{187}{The Crucifixion}

\qstart{Which event is described here: ``All of Golgotha was covered by thousands upon thousands of crosses upon which day by day there perished the flower of the Jewish race. A terrible harvest of the seed-sowing of this day [of Jesus' crucifixion]''?}
{The Roman siege of Jerusalem 40 years after crucificion}{1}
{The Babylonian siege leading to the Jews captivity}{0}
\qstop

\qstart{Why did the sky darken from midday on the day of Jesus' crucificion?}
{God's anger}{0}
{A hot wind sandstorm from Arabian desert was coming}{1}
{solar eclipse}{0}
\qstop

\qstart{Why did Jesus say, whilst on the cross, ``My God, my God, why have you forsaken me''?}
{He felt abandoned}{0}
{In his vanishing consciousness he was reciting Psalm 22}{1}
\qstop

\qstart{Give the time of Jesus' arrest and the time his so-called ``trial'' ended?}
{03:30 and 08:00}{1}
{06:00 and 12:00}{0}
{09:00 and 12:00}{0}
{06:00 and 18:00}{0}
\qstop

\qstart{How old was Jesus when he was crucified?}
{30 years}{0}
{33 years}{0}
{35 years}{1}
{36 years}{0}
{40 years}{0}
\qstop

\qstart{How far from the ground were the Master's feet whilst on the cross?}
{0.56m}{0}
{1m}{1}
{2m}{0}
{3m}{0}
\qstop

\qstart{Give the time of Jesus' crucifixion and the time at which he died}
{09:00 and 15:00}{1}
{12:00 and 18:00}{0}
{09:00 and 21:00}{0}
{10:00 and 11:00}{0}
\qstop

\qstart{Did Jesus carry the entire cross to Golgotha?}
{yes}{0}
{no, just the crossbeam}{1}
{no, someone else carried it}{0}
\qstop

\qstart{From whom did the Greeks and Romans learn of crucifixion as a method of execution?}
{The Phoenicians}{1}
{The Jews}{0}
{The Armenians}{0}
\qstop

\qstart{Who wrote the small white board to go above the head of Jesus on the cross and what did it say?}
{Pilate. ``Jesus of Nazareth --- the King of the Jews''. In Latin, Greek \&\ Aramaic}{1}
{Pilate. ``Traitor''. In Latin}{0}
{Annas \&\ Caiaphas. ``He said he is the King of the Jews''. In Hebrew}{0}
\qstop

\qstart{Which of these were at the foot of Jesus' cross during crucifixion?}
{Jude, Jesus' brother}{1}
{Ruth, Jesus' sister}{1}
{Mary Magdalene}{1}
{Rebecca}{1}
{John}{1}
{Peter}{0}
{Thomas}{0}
{James}{0}
\qstop

\qstart{Who carried Jesus' body for burial?}
{Joseph of Arimathea}{1}
{Nicodemus}{1}
{John Zebedee}{1}
{A Roman centurion}{1}
\qstop

\qstart{What was the last conscious thought of the human Jesus dying on the cross?}
{repetition of a portion of the Boom of Psalms now known as Psalms \#20, \#21 and \#22}{1}
{memories of his mother Mary}{0}
{memories of his brothers}{0}
{anxiety and fear about the future of Christianity}{0}
{fear about the future of the apostles}{0}
\qstop

\qpaper{188}{The Time of the Tomb}

\qstart{Why was Jesus buried in haste?}
{Because it was the Sabbath and preparations were on for the week of Passover}{1}
{It was the Jewish custom}{0}
{It was dark}{0}
{It was the Roman custom}{0}
\qstop

\qstart{How many stones were set in front of Jesus' tomb to stop his followers taking his body?}
{2}{1}
{7}{0}
{10}{0}
{12}{0}
{24}{0}
\qstop

\qstart{How many guards were placed around Jesus' tomb?}
{8 Roman guards}{0}
{5 Roman guards and 3 Jewish guards}{0}
{a Roman cohort}{0}
{a Roman legion}{0}
{10 Roman soldiers and 10 Jewish guards}{1}
{12 Roman soldiers and 7 Jewish guards}{0}
\qstop

\qpaper{189}{The Resurrection}

\qstart{What happened to the body of Jesus after his resurrection?}
{removed from the planet by the angels}{0}
{taken by the Jews and thrown into the pit for criminals}{0}
{dissolved by the technique of dematerialization by the angels}{0}
{stolen by the Apostles and burried privately}{0}
{dissolved by the process of accelerated time by the angels}{1}
{moved to Echmiadzin where it is now kept secretly}{0}
\qstop

\qstart{What was left in the tomb after the resurrection of Jesus?}
{Nothing, it was empty}{0}
{Linen sheet}{0}
{Napkin, bandages, and a linen sheet}{1}
\qstop

\qstart{When did Urantia's complete (planetary) dispensational roll calls (resurrections) take place?}
{At the arrival of the Planetary Prince}{0}
{At the time of Adam}{0}
{At the mortal transit of Jesus}{0}
{All three}{1}
\qstop

\qstart{Which of these women returned to Jesus' tomb after Sabbath to properly embalm him?}
{Mary Magdalene}{1}
{Mary Alpheus}{1}
{Salome Zebedee}{1}
{Joanna}{1}
{Susanna}{1}
{Mary the mother of Jesus}{0}
\qstop

\qstart{Who rolled away Jesus' tombstone?}
{Secondary Midwayers}{1}
{The resurrected Jesus}{0}
{Seraphim}{0}
{Primary Midwayers}{0}
{Melchizedeks}{0}
\qstop

\qstart{What did the guards see immediately after Jesus resurrected? }
{Nothing but the stone moving by itself}{1}
{Jesus walking out of the tomb}{0}
{Mighty angels moving the stone away}{0}
\qstop

\qstart{Who else was resurrected at the time of Jesus' resurrection?}
{The two thieves crucified with him}{0}
{The survivors of the human races since the days of Adam}{1}
{One of the two thieves crucified with him}{0}
\qstop

\qpaper{190}{Morontia Appearances of Jesus}

\qstart{How many appearances to mortals in total did Jesus make in morontia form?}
{0}{0}
{3}{0}
{7}{0}
{12}{0}
{19}{1}
{144}{0}
\qstop

\qstart{Does the morontia body have circulating blood and partake of ordinary material food?}
{yes}{0}
{no}{1}
\qstop

\qpaper{191}{Appearances to the Apostles and Other Leaders}

\qstart{Was Abner present at any of post-resurrection appearances of Jesus?}
{yes, the 10\ts{th} appearance}{1}
{no}{0}
\qstop

\qstart{Throughout Jesus' trials and crucifixion which two brothers played a leading role in relaying messages to Jesus' family, apostles and chief disciples?}
{Andrew \&\ Peter}{0}
{James \&\ Judas Alpheus}{0}
{James \&\ John Zebedee}{0}
{John \&\ David Zebedee}{1}
\qstop

\qpaper{192}{Appearances in Galilee}

\qpaper{193}{Final Appearances and Ascension}

\qpaper{194}{Bestowal of the Spirit of Truth}

\qstart{When was the Spirit of Truth bestowed upon Urantia?}
{16 May 30 A.D.}{0}
{18 May 30 A.D.}{0}
{28 May 30 A.D.}{1}
\qstop

\qstart{Why is Pentecost called thus?}
{Greek word for the number 50}{1}
{Greek word for the number 40}{0}
\qstop

\qstart{No special gift was bestowed upon the members of Jesus’ earthly family. Pentecost marked the end of special priesthoods and all belief in sacred families. TRUE or FALSE?}
{FALSE}{0}
{TRUE}{1}
\qstop

\qstart{When was Jesus of Nazareth resurrected?}
{9 April 30 A.D.}{1}
{10 April 30 A.D.}{0}
{18 April 33 A.D.}{0}
{20 April 33 A.D.}{0}
\qstop

\qpaper{195}{After Pentecost}

\qstart{Which version of Jesus' message was more true to his teachings?}
{Eastern}{1}
{Western (Hellenized)}{0}
\qstop

\qstart{Which version of Jesus' message was eventually lost in the Islamic movement?}
{Eastern (Abner)}{1}
{Western}{0}
\qstop

\qpaper{196}{The Faith of Jesus}
